---
title: "cca_behav_quest"
author: "Aamir Sohail"
date: "2025-01-11"
output: html_document
---

# Description of this script

This script runs the canonical correlation analyses between three sets of canonical variates (CVs):

1. A behavioural CV containing:
* Switch frequency under dissenting group consensus (lower % indicates pro-self-behaviour)
* Stay frequency under confirming group consensus (lower % indicates pro-self-behaviour)
* Bet difference under confirming consensus (positive values indicate increased confidence)
* Bet difference under dissenting consensus (negative values indicate decreased confidence)

2. A questionnaire CV consisting scores from each of the subscales of the questionnaire battery

## Set-up and installation

```{r setup, include=FALSE, message=FALSE, cache=TRUE, error=FALSE}
# Install packages only if they are not already installed
required_packages <- c("CCA", "tidyverse", "yacca", "ggplot2", "CCP", "PMA", 
                      "gridExtra", "here", "MVN", "corrplot", "mvtnorm", "boot", "caret", "moments")
install_if_missing <- required_packages[!required_packages %in% installed.packages()]
if (length(install_if_missing) > 0) {
  install.packages(install_if_missing, quietly = TRUE)
}

# Load libraries
library(CCA)
library(ggplot2)
library(tidyverse)
library(yacca)
library(CCP)
library(PMA)
library(gridExtra)
library(dplyr)
library(knitr)
library(here)
library(MVN)
library(corrplot)
library(mvtnorm)
library(boot)
library(caret)
library(moments)
```

Plot a correlation matrix of questionnaire scores

```{r}
rm(list=ls())

# Read and process data
merged_data <- read_csv(here("data", "preprocessed", "merged_test_data.csv"), show_col_types = FALSE)

# Create correlation matrix dataframe with one row per participant
questionnaire_data <- merged_data %>%
  group_by(participant.id_in_session) %>%
  slice(1) %>%  # Take first instance of each participant
  select(ssms, dass, lsas, srp_sf, ami, aq_10) %>%
  ungroup()

# Calculate correlation matrix
cor_matrix <- cor(questionnaire_data, method = "pearson")

# If you want p-values for the correlations
cor_test <- psych::corr.test(questionnaire_data)

# Visualize using corrplot
corrplot(cor_matrix, 
         method = "color",
         type = "upper",
         addCoef.col = "black",
         number.cex = 0.7,
         tl.col = "black",
         tl.srt = 45,
         diag = FALSE)
```

## Behavioural-Questionnaire CCA

Run the CCA between the behavioural and questionnaire CV's

```{r setup, include=FALSE, message=FALSE}
rm(list=ls())

# Source the core pipeline functions
source(here("R", "cca.R"))

# Read and prepare data
merged_data <- read_csv(here("data", "preprocessed", "merged_test_data.csv"), 
                       show_col_types = FALSE)

# Prepare behavioral CV data
behavioral_data <- merged_data %>%
  group_by(participant.id_in_session) %>%
  summarise(
    switch_dissent = mean(player.switch_vs_stay[player.choice1_with < 0.5]) * 100,
    stay_confirm = mean(1 - player.switch_vs_stay[player.choice1_with >= 0.5]) * 100,
    bet_diff_confirm = mean(player.bet2[player.choice1_with >= 0.5] - 
                          player.bet1[player.choice1_with >= 0.5]),
    bet_diff_dissent = mean(player.bet2[player.choice1_with < 0.5] - 
                          player.bet1[player.choice1_with < 0.5])
  )

# Prepare questionnaire CV data
questionnaire_data <- merged_data %>%
  group_by(participant.id_in_session) %>%
  slice(1) %>%  
  select(
         lsas_p, lsas_s, 
         dass_a, dass_d, dass_s,
         ssms_cd, ssms_ia,
         srp_sf_ipm, srp_sf_ca, srp_sf_els, srp_sf_ct,
         ami_es, ami_sm, ami_ba,
         aq_10
  ) %>%
  ungroup()

# Merge and z-score
cca_data <- behavioral_data %>%
  left_join(questionnaire_data, by = "participant.id_in_session") %>%
  select(-participant.id_in_session)
 
cca_data_scaled <- scale(cca_data) %>% as.data.frame()

# Prepare matrices for CCA
X <- as.matrix(cca_data_scaled[, 1:4])  # Behavioral variables
Y <- as.matrix(cca_data_scaled[, 5:19])  # Questionnaire variables

# Create correlation matrix dataframe with one row per participant
questionnaire_data <- merged_data %>%
  group_by(participant.id_in_session) %>%
  slice(1) %>%  
  select(ssms, dass, lsas, srp_sf, ami, aq_10) %>%
  ungroup()

# Calculate correlation matrix
cor_matrix <- cor(questionnaire_data, method = "pearson")

# Visualize using corrplot
corrplot(cor_matrix, 
         method = "color",
         type = "upper",
         addCoef.col = "black",
         number.cex = 0.7,
         tl.col = "black",
         tl.srt = 45,
         diag = FALSE)

# Set output directory
output_dir <- here("output", "cca", "behavioural_questionnaire_cca")

# Run CCA analysis
results <- run_cca_analysis(X, Y, output_dir)
```

