---
title: "otree_data_preprocessing_single"
author: "Aamir Sohail"
date: "2025-02-06"
output: html_document
---

```{r setup, include=FALSE}

# Install packages only if they are not already installed
required_packages <- c("ggplot2", "tidyverse", "readr", "here", "ggstatsplot")
install_if_missing <- required_packages[!required_packages %in% installed.packages()]
if (length(install_if_missing) > 0) {
  install.packages(install_if_missing, quietly = TRUE)
}

# Load required libraries
library(tidyverse)
library(ggplot2)
library(readr)
library(here)
library(ggstatsplot)
```

# Submission data checks (for feedback values)

First let's combine submission data for checks
```{r}
rm(list=ls())

# Read the CSV files
data <- read_csv(here("data", "raw", "otree", "session_10_1200_3_3_25", "orig_ids", "submission_2025-03-03.csv"), 
                    show_col_types = FALSE)

# Only get the current session (i.e., only keep rows where the session code is the current one)
# In this case, only keep rows where session.code = karawteb
data <- data %>%
  filter(session.code == "3yhym2ig")

# Bind the datasets and select specific columns
data %>%
  # Filter for non-NA main_task_bonus
  filter(!is.na(player.main_task_bonus)) %>%
  # Select specific columns
  select(participant.id_in_session,
         participant.code,
         participant.label,
         player.id_in_group,
         player.main_task_bonus,
         player.task_understanding,
         player.task_difficulty,
         player.engagement,
         player.influence,
         player.real_players,
         player.attention_focus)

# Reshape the combined_data to long format
long_data <- data %>%
  select(player.task_understanding, 
         player.task_difficulty, 
         player.engagement, 
         player.influence, 
         player.real_players, 
         player.attention_focus) %>%
  pivot_longer(cols = everything(),
               names_to = "measure",
               values_to = "score") %>%
  mutate(measure = str_remove(measure, "player."))

# Calculate means
means <- long_data %>%
  group_by(measure) %>%
  summarise(mean_score = mean(score, na.rm = TRUE))

# Create the plot
ggplot(long_data, aes(x = measure, y = score)) +
  geom_violin(fill = "gray90", alpha = 0.5) +
  geom_point(data = means, aes(y = mean_score), 
             color = "red", size = 3) +
  geom_text(data = means, 
            aes(y = 110, label = sprintf("%.1f", mean_score)),  # Fixed position at y=110
            size = 4.5) +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    
    plot.margin = margin(1, 0.5, 0.5, 1, "cm")
  ) +
  labs(x = NULL,
       y = "Score",
       title = NULL) +
  scale_y_continuous(limits = c(-5, 120))  # Increased to make room for labels at 110
```

# Main task data preprocessing

Now let's combine the main task data
```{r}
rm(list=ls())

# Read the CSV files›
data <- read_csv(here("data", "raw", "otree", "session_10_1200_3_3_25", "orig_ids", "main_task_2025-03-03.csv"), 
                   show_col_types = FALSE)

# Again, only keep rows where the session code is the current one 
data <- data %>%
  filter(session.code == "e78bi334")

# Remove unneeded columns
data <- data[, !(names(data) %in% c(
  "participant._is_bot", "participant._index_in_pages", "player.last_check_time",
  "participant._max_page_index", "participant._current_app_name", 
  "participant._current_page_name", "participant.time_started_utc",
  "participant.visited", "participant.mturk_worker_id",
  "participant.mturk_assignment_id", "participant.payoff",
  "player.role", "player.payoff", "player.consecutive_missed_checks",
  "player.individual_page_load_time", "player.base_payoff",
  "player.manual_second_choice", "player.disconnection_streak",
  "player.is_bot", "player.last_connection_time", "player.last_check_time",
  "group.current_round", "group.second_bet_timer_ended_executed",
  "group.next_round_transition_time", "group.reversal_rounds",
  "group.bet_container_displayed", "group.remaining_images_displayed",
  "group.round_reward_set", "group.intertrial_interval", "group.all_players_loaded",
  "group.players_loaded_count", "group.disconnected_players",
  "group.bot_players", "group.active_bots",
  "group.disconnection_streaks", "session.code",
  "session.label", "session.mturk_HITId",
  "session.mturk_HITGroupId", "session.comment",
  "session.is_demo"
))]


# Convert rewards to -1 and 1 instead of 0 and 1
data$player.trial_reward[data$player.trial_reward == 0] <- -1
data$player.loss_or_gain[data$player.loss_or_gain == 0] <- -1
data$player.player1_loss_or_gain[data$player.player1_loss_or_gain == 0] <- -1
data$player.player2_loss_or_gain[data$player.player2_loss_or_gain == 0] <- -1
data$player.player3_loss_or_gain[data$player.player3_loss_or_gain == 0] <- -1
data$player.player4_loss_or_gain[data$player.player4_loss_or_gain == 0] <- -1

# Remove the first trial
data_filtered <- data[data$group.trial_number != 1, ]

# Subtract 1 from group.trial_number and subsession.round_number
data_filtered$group.trial_number <- data_filtered$group.trial_number - 1
data_filtered$subsession.round_number <- data_filtered$subsession.round_number - 1

# Reassign to data
data <- data_filtered

# Convert choice with/against to decimals instead of raw numbers
# Create a function to apply the division
divide_by_4 <- function(x) {
  ifelse(x == 0, 0, x/4)
}

# Apply the transformation to each column
data$player.choice1_with <- divide_by_4(data$player.choice1_with)
data$player.choice1_against <- divide_by_4(data$player.choice1_against)
data$player.choice2_with <- divide_by_4(data$player.choice2_with)
data$player.choice2_against <- divide_by_4(data$player.choice2_against)
```

Remove trials where the player left and list the number of trials per participant
```{r}
# Remove trials where the player left
data <- data %>% 
  filter(!is.na(player.my_page_load_time))

# List the number of trials per participant
data %>%
  count(participant.id_in_session) %>%
  arrange(participant.id_in_session)
```

Remove participants who didn't complete the task
```{r}
# Remove participants with too few trials
data <- data %>%
  group_by(participant.id_in_session) %>%
  filter(n() >= 63) %>%
  ungroup()

# List the number of trials per participant after filtering
data %>%
  count(participant.id_in_session) %>%
  arrange(participant.id_in_session)
```


Save the preprocessed data
```{r}
# Save the preprocessed data (remove pilots if not a pilot)
write_csv(data, here("data", "preprocessed", "otree", "sessions", "single", "single_main_task_03_03_1200.csv"))
```

# Main task data checks and exclusions 

Load in the data
```{r}
rm(list=ls())

data <- read_csv(here("data", "preprocessed", "otree", "sessions", "single", "single_main_task_03_03_1200.csv"), show_col_types = FALSE)
```


Run several checks, including:

Check the number of manual responses per participant (choices and bets)
Check the total number of trials where all choices and bets were made manually
Check the number of times image A and image B was selected manually
Check the average manual bet 1 and bet 2

```{r}
summary_df <- data %>%
  group_by(participant.id_in_session, participant.label) %>%
  summarise(
    sum_choice_one = sum(player.computer_choice_one, na.rm = TRUE),
    sum_choice_two = sum(player.computer_choice_two, na.rm = TRUE),
    sum_bet_one = sum(player.computer_bet_one, na.rm = TRUE),
    sum_bet_two = sum(player.computer_bet_two, na.rm = TRUE),
    
    # Separate counts for manual trials of each type
    manual_choice_one_trials = sum(player.computer_choice_one == 0, na.rm = TRUE),
    manual_choice_two_trials = sum(player.computer_choice_two == 0, na.rm = TRUE),
    manual_bet_one_trials = sum(player.computer_bet_one == 0, na.rm = TRUE),
    manual_bet_two_trials = sum(player.computer_bet_two == 0, na.rm = TRUE),
    
    # Count trials where computer_choice is 0
    count_choice_one_zero = sum(player.computer_choice_one == 0, na.rm = TRUE),
    count_choice_two_zero = sum(player.computer_choice_two == 0, na.rm = TRUE),
    
    # Count 1s and 2s only when respective computer_choice is 0
    count_ones_image_one = sum(player.chosen_image_one_binary == '1' & 
                              player.computer_choice_one == 0, na.rm = TRUE),
    count_twos_image_one = sum(player.chosen_image_one_binary == '2' & 
                              player.computer_choice_one == 0, na.rm = TRUE),
    count_ones_image_two = sum(player.chosen_image_two_binary == '1' & 
                              player.computer_choice_two == 0, na.rm = TRUE),
    count_twos_image_two = sum(player.chosen_image_two_binary == '2' & 
                              player.computer_choice_two == 0, na.rm = TRUE),
    
    # Average bets when computer bets are 0
    avg_bet_one = mean(player.bet1[player.computer_bet_one == 0], na.rm = TRUE),
    avg_bet_two = mean(player.bet2[player.computer_bet_two == 0], na.rm = TRUE)
  )

# Create separate dataframes for each type of response with too few manual trials
low_choice_one_participants <- summary_df %>%
  filter(manual_choice_one_trials < 45) %>%
  select(participant.id_in_session, participant.label, manual_choice_one_trials) %>%
  mutate(Reason = "Too few manual choice one trials")

low_choice_two_participants <- summary_df %>%
  filter(manual_choice_two_trials < 45) %>%
  select(participant.id_in_session, participant.label, manual_choice_two_trials) %>%
  mutate(Reason = "Too few manual choice two trials")

low_bet_one_participants <- summary_df %>%
  filter(manual_bet_one_trials < 40) %>%
  select(participant.id_in_session, participant.label, manual_bet_one_trials) %>%
  mutate(Reason = "Too few manual bet one trials")

low_bet_two_participants <- summary_df %>%
  filter(manual_bet_two_trials < 40) %>%
  select(participant.id_in_session, participant.label, manual_bet_two_trials) %>%
  mutate(Reason = "Too few manual bet two trials")

# Print results for each type
cat("Participants with fewer than 45 manual choice one trials:\n")
print(low_choice_one_participants)
cat("\nParticipants with fewer than 45 manual choice two trials:\n")
print(low_choice_two_participants)
cat("\nParticipants with fewer than 40 manual bet one trials:\n")
print(low_bet_one_participants)
cat("\nParticipants with fewer than 40 manual bet two trials:\n")
print(low_bet_two_participants)

# Combine participants who have too few trials in either choice one or choice two
combined_low_choices <- bind_rows(low_choice_one_participants, low_choice_two_participants, low_bet_one_participants, low_bet_two_participants) %>%
  distinct(participant.id_in_session, .keep_all = TRUE)

# Save to CSV
write.csv(combined_low_choices,
          file = "excluded_otree_subjects.csv",
          row.names = FALSE)

cat("Number of participants excluded:", nrow(combined_low_choices))
```

Get the participants with too many choices of the same image
```{r}
# First save the results from the first check
write.csv(combined_low_choices,
          file = "excluded_otree_subjects.csv",
          row.names = FALSE)
cat("Number of participants excluded in first check:", nrow(combined_low_choices), "\n")

# Read existing data, ensuring it has the correct structure
if(file.exists("excluded_otree_subjects.csv")) {
  existing_data <- read.csv("excluded_otree_subjects.csv")
  
  # If file exists but is empty (no rows), create proper structure
  if(nrow(existing_data) == 0) {
    existing_data <- data.frame(
      participant.id_in_session = integer(),
      participant.label = character(),
      manual_choice_one_trials = numeric(),
      manual_choice_two_trials = numeric(),
      Reason = character(),
      stringsAsFactors = FALSE
    )
  }
} else {
  # If file doesn't exist, create empty data frame with correct structure
  existing_data <- data.frame(
    participant.id_in_session = integer(),
    participant.label = character(),
    manual_choice_one_trials = numeric(),
    manual_choice_two_trials = numeric(),
    Reason = character(),
    stringsAsFactors = FALSE
  )
}

# Second check for extreme choice patterns
high_ones_participants <- summary_df %>%
  filter(count_ones_image_one > 48 | count_ones_image_one < 16) %>%
  select(participant.id_in_session, participant.label, count_ones_image_one) %>%
  mutate(
    manual_choice_one_trials = NA,
    manual_choice_two_trials = NA,
    Reason = "Too many/few choices of the same image"
  )

# Print to console
cat("Participants with extreme choice patterns (count_ones_image_one > 50 or < 16):\n")
print(high_ones_participants)

# Combine and write back to CSV
combined_data <- bind_rows(existing_data, high_ones_participants) %>%
  distinct(participant.id_in_session, .keep_all = TRUE)

write.csv(combined_data, 
          file = "excluded_otree_subjects.csv",
          row.names = FALSE)

cat("Total number of participants excluded:", nrow(combined_data), "\n")
```


Remove participants with too few manual trials and too many choices of the same image

```{r}
# Read the CSV with excluded participants
excluded_participants <- read.csv("excluded_otree_subjects.csv") %>%
  distinct(participant.label)  # Get unique participant labels

# Filter out these participants from the main data
filtered_data <- data %>%
  filter(!participant.label %in% excluded_participants$participant.label)

# Print how many participants were excluded
cat("Number of participants excluded:", nrow(excluded_participants), "\n")

write_csv(filtered_data, here("data", "preprocessed", "otree", "sessions", "main_task_filtered_03_03_1200.csv"))
```


# Perform basic checks and visualizations of the cleaned oTree data

Load the filtered data
```{r}
rm(list=ls())

data <- read_csv(here("data", "preprocessed", "otree", "sessions", "main_task_filtered_03_03_1200.csv"), show_col_types = FALSE)
```


Re-calculate the checks from before:

- Check the number of manual responses per participant (choices and bets)
- Check the total number of trials where all choices and bets were made manually
- Check the number of times image A and image B was selected manually
- Check the average manual bet 1 and bet 2

```{r}
summary_df <- data %>%
  group_by(participant.id_in_session, participant.label) %>%
  summarise(
    sum_choice_one = sum(player.computer_choice_one, na.rm = TRUE),
    sum_choice_two = sum(player.computer_choice_two, na.rm = TRUE),
    sum_bet_one = sum(player.computer_bet_one, na.rm = TRUE),
    sum_bet_two = sum(player.computer_bet_two, na.rm = TRUE),
    
    # Separate counts for manual trials of each type
    manual_choice_one_trials = sum(player.computer_choice_one == 0, na.rm = TRUE),
    manual_choice_two_trials = sum(player.computer_choice_two == 0, na.rm = TRUE),
    manual_bet_one_trials = sum(player.computer_bet_one == 0, na.rm = TRUE),
    manual_bet_two_trials = sum(player.computer_bet_two == 0, na.rm = TRUE),
    
    # Count trials where computer_choice is 0
    count_choice_one_zero = sum(player.computer_choice_one == 0, na.rm = TRUE),
    count_choice_two_zero = sum(player.computer_choice_two == 0, na.rm = TRUE),
    
    # Count 1s and 2s only when respective computer_choice is 0
    count_ones_image_one = sum(player.chosen_image_one_binary == '1' & 
                              player.computer_choice_one == 0, na.rm = TRUE),
    count_twos_image_one = sum(player.chosen_image_one_binary == '2' & 
                              player.computer_choice_one == 0, na.rm = TRUE),
    count_ones_image_two = sum(player.chosen_image_two_binary == '1' & 
                              player.computer_choice_two == 0, na.rm = TRUE),
    count_twos_image_two = sum(player.chosen_image_two_binary == '2' & 
                              player.computer_choice_two == 0, na.rm = TRUE),
    
    # Average bets when computer bets are 0
    avg_bet_one = mean(player.bet1[player.computer_bet_one == 0], na.rm = TRUE),
    avg_bet_two = mean(player.bet2[player.computer_bet_two == 0], na.rm = TRUE)
  )

# Calculate group averages
group_averages <- summary_df %>%
  summarise(
    avg_manual_choice_one = mean(manual_choice_one_trials, na.rm = TRUE),
    avg_manual_choice_two = mean(manual_choice_two_trials, na.rm = TRUE),
    avg_manual_bet_one = mean(manual_bet_one_trials, na.rm = TRUE),
    avg_manual_bet_two = mean(manual_bet_two_trials, na.rm = TRUE)
  )

# Reshape the data to long format for plotting
plot_data <- summary_df %>%
  select(participant.id_in_session, 
         manual_choice_one_trials, 
         manual_choice_two_trials, 
         manual_bet_one_trials, 
         manual_bet_two_trials) %>%
  pivot_longer(cols = starts_with("manual"),
               names_to = "response_type",
               values_to = "count") %>%
  mutate(response_type = factor(response_type,
                               levels = c("manual_choice_one_trials",
                                        "manual_choice_two_trials",
                                        "manual_bet_one_trials",
                                        "manual_bet_two_trials"),
                               labels = c("Choice 1",
                                        "Choice 2",
                                        "Bet 1",
                                        "Bet 2")))

# Create the violin plot
ggplot(plot_data, aes(x = response_type, y = count)) +
  geom_violin(fill = "lightblue", alpha = 0.5) +
  geom_jitter(width = 0.2, alpha = 0.4, color = "darkblue") +
  geom_boxplot(width = 0.1, alpha = 0.2, outlier.shape = NA) +
  theme_minimal() +
  labs(x = "Response Type",
       y = "Number of Manual Responses",
       title = "Distribution of Manual Responses by Type") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Plot the number of time image 1 was chosen manually, and the average bet sizes
```{r}
# Reshape data for the count_ones plot
counts_data <- summary_df %>%
  select(participant.id_in_session, count_ones_image_one, count_ones_image_two) %>%
  pivot_longer(cols = c(count_ones_image_one, count_ones_image_two),
               names_to = "choice_type",
               values_to = "count")

# Rest of your original code...
bets_data <- summary_df %>%
  select(participant.id_in_session, avg_bet_one, avg_bet_two) %>%
  pivot_longer(cols = c(avg_bet_one, avg_bet_two),
               names_to = "bet_type",
               values_to = "average_bet")

# Create violin plot for count_ones
count_plot <- ggbetweenstats(
  data = counts_data,
  x = choice_type,
  y = count,
  title = "Distribution of '1' Choices by Image Type",
  xlab = "Choice Type",
  ylab = "Count of '1' Choices",
  type = "nonparametric",
  package = "ggsci",
  palette = "nrc_npg",
  messages = FALSE
)

# Create violin plot for average bets
bets_plot <- ggbetweenstats(
  data = bets_data,
  x = bet_type,
  y = average_bet,
  title = "Distribution of Average Bets",
  xlab = "Bet Type",
  ylab = "Average Bet",
  type = "nonparametric",
  package = "ggsci",
  palette = "nrc_npg",
  messages = FALSE
)

# Display plots
count_plot
bets_plot
```

Calculate and plot the proportion of each image chosen for each block for both choices, and the accuracy
Ideally, you would expect for the proportion of each image chosen to be around 0.6-0.7 for each block
```{r}
# Function to process data and create plots and tables
analyze_choices <- function(data, choice_column, computer_column, prop_title) {
  # Calculate proportions, counts, and accuracy
  participant_blocks <- data %>%
    filter(!!sym(computer_column) == 0) %>%
    mutate(block = case_when(
      subsession.round_number <= 15 ~ "1-15",
      subsession.round_number <= 32 ~ "16-32",
      subsession.round_number <= 47 ~ "33-47",
      TRUE ~ "48-64"
    )) %>%
    group_by(participant.id_in_session, block) %>%
    summarize(
      ones_count = sum(!!sym(choice_column) == 1),
      twos_count = sum(!!sym(choice_column) == 2),
      total_trials = n(),
      prop_ones = mean(!!sym(choice_column) == 1),
      prop_twos = mean(!!sym(choice_column) == 2),
      .groups = 'drop'
    ) %>%
    mutate(
      ones_fraction = sprintf("%d/%d", ones_count, total_trials),
      twos_fraction = sprintf("%d/%d", twos_count, total_trials),
      accuracy = case_when(
        block %in% c("1-15", "33-47") ~ prop_ones,
        block %in% c("16-32", "48-64") ~ prop_twos
      )
    )
  
  # Create counts table
  counts_table <- participant_blocks %>%
    select(participant.id_in_session, block, ones_fraction, twos_fraction)
  
  # Create final dataset for choice plotting
  blocks_final <- participant_blocks %>%
    pivot_longer(
      cols = c(prop_ones, prop_twos),
      names_to = "choice",
      values_to = "proportion"
    )
  
  # Run paired t-tests for choices
  significance_tests <- blocks_final %>%
    group_by(block) %>%
    summarize(
      p_value = t.test(
        proportion[choice == "prop_ones"],
        proportion[choice == "prop_twos"],
        paired = TRUE
      )$p.value,
      significance = case_when(
        p_value < 0.001 ~ "***",
        p_value < 0.01 ~ "**",
        p_value < 0.05 ~ "*",
        TRUE ~ "ns"
      ),
      y_pos = max(proportion) + 0.1
    )
  
  # Create choice plot
  choice_plot <- ggplot(blocks_final, aes(x = block, y = proportion, color = choice)) +
    geom_jitter(width = 0.2, alpha = 0.5) +
    stat_summary(fun = mean, geom = "point", size = 3) +
    stat_summary(fun = mean, geom = "line", aes(group = choice)) +
    geom_text(data = significance_tests, 
              aes(x = block, y = y_pos, label = significance),
              color = "black") +
    theme_minimal() +
    labs(
      title = prop_title,
      x = "Trial Block",
      y = "Proportion",
      color = "Choice"
    ) +
    scale_color_manual(
      values = c("prop_ones" = "blue", "prop_twos" = "red"),
      labels = c("prop_ones" = "Ones", "prop_twos" = "Twos")
    )
  
  return(list(plot = choice_plot, 
             data = participant_blocks,
             counts = counts_table))
}

# Function to process accuracy data
process_accuracy_data <- function(data, choice_column, computer_column, choice_label) {
  participant_blocks <- data %>%
    filter(!!sym(computer_column) == 0) %>%
    mutate(block = case_when(
      subsession.round_number <= 15 ~ "1-15",
      subsession.round_number <= 32 ~ "16-32",
      subsession.round_number <= 47 ~ "33-47",
      TRUE ~ "48-64"
    )) %>%
    group_by(participant.id_in_session, block) %>%
    summarize(
      ones_count = sum(!!sym(choice_column) == 1),
      twos_count = sum(!!sym(choice_column) == 2),
      total_trials = n(),
      prop_ones = mean(!!sym(choice_column) == 1),
      prop_twos = mean(!!sym(choice_column) == 2),
      .groups = 'drop'
    ) %>%
    mutate(
      accuracy = case_when(
        block %in% c("1-15", "33-47") ~ prop_ones,
        block %in% c("16-32", "48-64") ~ prop_twos
      ),
      choice_type = choice_label
    )
  
  return(participant_blocks)
}

# Run analyses for proportion plots
results_one <- analyze_choices(data, 
                             "player.chosen_image_one_binary", 
                             "player.computer_choice_one", 
                             "Proportion of 1's and 2's by Block (First Choice)")
results_two <- analyze_choices(data, 
                             "player.chosen_image_two_binary", 
                             "player.computer_choice_two", 
                             "Proportion of 1's and 2's by Block (Second Choice)")

# Process data for accuracy plot
accuracy_one <- process_accuracy_data(data, 
                                    "player.chosen_image_one_binary", 
                                    "player.computer_choice_one", 
                                    "First Choice")
accuracy_two <- process_accuracy_data(data, 
                                    "player.chosen_image_two_binary", 
                                    "player.computer_choice_two", 
                                    "Second Choice")

# Combine accuracy data
combined_accuracy <- rbind(accuracy_one, accuracy_two)

# Create combined accuracy plot
accuracy_plot <- ggplot(combined_accuracy, 
                       aes(x = block, y = accuracy, color = choice_type)) +
  geom_jitter(width = 0.2, alpha = 0.3) +
  stat_summary(fun = mean, geom = "point", size = 3) +
  stat_summary(fun = mean, geom = "line", aes(group = choice_type)) +
  theme_minimal() +
  labs(
    title = "Mean Accuracy by Block for Both Choices",
    x = "Trial Block",
    y = "Accuracy",
    color = "Choice"
  ) +
  scale_color_manual(values = c("First Choice" = "blue", "Second Choice" = "red"))

# Display plots
results_one$plot
results_two$plot
accuracy_plot

# Display tables
print("Counts for First Choice:")
print(results_one$counts)
print("Counts for Second Choice:")
print(results_two$counts)
```

Reaction time for manual choices and bets
```{r}
# Calculate timing means with specific column order
timing_summary_df <- data %>%
  group_by(participant.id_in_session) %>%
  summarise(
    mean_initial_choice_time = mean(player.initial_choice_time[player.computer_choice_one == 0], na.rm = TRUE),
    mean_initial_bet_time = mean(player.initial_bet_time[player.computer_bet_one == 0], na.rm = TRUE),
    mean_second_choice_time = mean(player.second_choice_time[player.computer_choice_two == 0], na.rm = TRUE),
    mean_second_bet_time = mean(player.second_bet_time[player.computer_bet_two == 0], na.rm = TRUE)
  )

# Create a manual ordering vector
order_levels <- c("mean_initial_choice_time", 
                 "mean_initial_bet_time",
                 "mean_second_choice_time", 
                 "mean_second_bet_time")

nice_labels <- c("Initial Choice Time",
                "Initial Bet Time",
                "Second Choice Time",
                "Second Bet Time")

# Reshape data for plotting
timing_data <- timing_summary_df %>%
  pivot_longer(cols = -participant.id_in_session,
               names_to = "timing_type",
               values_to = "time") %>%
  mutate(timing_type = factor(timing_type, 
                             levels = order_levels,
                             labels = nice_labels))

# Create violin plot
ggbetweenstats(
  data = timing_data,
  x = timing_type,
  y = time,
  title = "Distribution of Response Times",
  xlab = "Response Type",
  ylab = "Time (seconds)",
  type = "nonparametric",
  package = "ggsci",
  palette = "nrc_npg",
  messages = FALSE
) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Reaction time for manual choices and bets across blocks

```{r}
# Create a function to process and plot reaction times
plot_reaction_times <- function(data, time_column, computer_column, title) {
  # Filter and prepare data
  rt_data <- data %>%
    filter(!!sym(computer_column) == 0) %>%
    filter(!!sym(time_column) <= 3) %>%  # Filter out trials => 3 seconds
    mutate(block = case_when(
      subsession.round_number <= 15 ~ "1-15",
      subsession.round_number <= 32 ~ "16-32",
      subsession.round_number <= 47 ~ "33-47",
      TRUE ~ "48-64"
    )) %>%
    # Calculate participant averages per block
    group_by(participant.id_in_session, block) %>%
    summarise(
      avg_rt = mean(!!sym(time_column), na.rm = TRUE)
    ) %>%
    ungroup() %>%
    # Convert block to factor to maintain order
    mutate(block = factor(block, levels = c("1-15", "16-32", "33-47", "48-64")))

  # Create violin plot using ggbetweenstats
  plot <- ggbetweenstats(
    data = rt_data,
    x = block,
    y = avg_rt,
    type = "nonparametric",
    plot.type = "violin",
    title = title,
    xlab = "Trial Block",
    ylab = "Average Response Time (seconds)",
    violin.args = list(width = 0.5, alpha = 0.4),
    point.args = list(
      alpha = 0.5, 
      size = 2,
      position = position_jitter(width = 0.2, seed = 123)  # Add more jitter
    ),
    results.subtitle = FALSE,
    pairwise.comparisons = FALSE
  )
  
  return(plot)
}

# Generate all four plots
initial_choice_plot <- plot_reaction_times(
  data,
  "player.initial_choice_time",
  "player.computer_choice_one",
  "Initial Choice Response Times by Block"
)
second_choice_plot <- plot_reaction_times(
  data,
  "player.second_choice_time",
  "player.computer_choice_two",
  "Second Choice Response Times by Block"
)
initial_bet_plot <- plot_reaction_times(
  data,
  "player.initial_bet_time",
  "player.computer_bet_one",
  "Initial Bet Response Times by Block"
)
second_bet_plot <- plot_reaction_times(
  data,
  "player.second_bet_time",
  "player.computer_bet_two",
  "Second Bet Response Times by Block"
)

# Display all plots
initial_choice_plot
second_choice_plot
initial_bet_plot
second_bet_plot
```

Cumulative earnings over trials from choice 2
```{r}
# First, create a starting point dataframe
start_points <- data %>%
  select(participant.id_in_session) %>%
  distinct() %>%
  mutate(subsession.round_number = 0,
         player.choice2_sum_earnings = 0)

# Combine with original data
data_with_start <- bind_rows(start_points, data)

# Now use this in the plot
ggplot() +
  # Individual participant lines with high transparency
  geom_line(data = data_with_start, 
            aes(x = subsession.round_number, 
                y = player.choice2_sum_earnings, 
                group = participant.id_in_session,
                color = factor(participant.id_in_session)),
            alpha = 0.2) +
  # Smoothed mean line with standard error
  geom_smooth(data = data_with_start,
             aes(x = subsession.round_number, y = player.choice2_sum_earnings),
             color = "blue",
             size = 1.5,
             se = TRUE,
             method = "loess") +
  # Vertical lines
  geom_vline(xintercept = 16, linetype = "dashed", color = "red") +
  geom_vline(xintercept = 33, linetype = "dashed", color = "red") +
  geom_vline(xintercept = 48, linetype = "dashed", color = "red") +
  labs(title = "Cumulative Score Over Trials by Participant (Choice 2 Outcome)",
       subtitle = "Blue line shows smoothed mean score with standard error bands",
       x = "Trial Number",
       y = "Score") +
  theme_minimal() +
  theme(legend.position = "none")
```

# Testing to see if players make choices significantly different from chance

Read the combined main task data from above
```{r}
rm(list=ls())

data <- read_csv(here("data", "preprocessed", "otree", "sessions", "main_task_filtered_03_03_1200.csv"), show_col_types = FALSE)
```

Check player choice accuracy across valid trials for both choices combined
```{r}
# Calculate the player choice accuracy across valid trials
summary_df <- data %>%
  group_by(participant.id_in_session) %>%
  summarise(
    total_choice1_accuracy = sum(ifelse(player.computer_choice_one != 1, player.choice1_accuracy, 0), na.rm = TRUE),
    total_choice2_accuracy = sum(ifelse(player.computer_choice_two != 1, player.choice2_accuracy, 0), na.rm = TRUE),
    number_of_trials = n(),
    valid_trials_choice1 = sum(player.computer_choice_one != 1),
    valid_trials_choice2 = sum(player.computer_choice_two != 1)
  )
```

Run binomial tests to check if the player choice accuracy is significantly different from chance, for choice 1 and choice 2 separately and combined
```{r}
# Add binomial test results and percentage accuracy for all three categories
summary_df <- summary_df %>%
  mutate(
    # Choice 1
    percentage_accuracy_choice1 = (total_choice1_accuracy / valid_trials_choice1) * 100,
    binom_p_value_choice1 = map2_dbl(
      total_choice1_accuracy, valid_trials_choice1,
      ~binom.test(.x, .y, p = 0.5)$p.value
    ),
    # Choice 2
    percentage_accuracy_choice2 = (total_choice2_accuracy / valid_trials_choice2) * 100,
    binom_p_value_choice2 = map2_dbl(
      total_choice2_accuracy, valid_trials_choice2,
      ~binom.test(.x, .y, p = 0.5)$p.value
    ),
    # Combined (keeping your existing calculations)
    total_combined_accuracy = total_choice1_accuracy + total_choice2_accuracy,
    total_valid_trials = valid_trials_choice1 + valid_trials_choice2,
    percentage_accuracy_combined = (total_combined_accuracy / total_valid_trials) * 100,
    binom_p_value_combined = map2_dbl(
      total_combined_accuracy, total_valid_trials,
      ~binom.test(.x, .y, p = 0.5)$p.value
    )
  )

# Look at significant results for all three categories
significant_results <- summary_df %>%
  summarise(
    significant_choice1 = sum(binom_p_value_choice1 < 0.05, na.rm = TRUE),
    significant_choice2 = sum(binom_p_value_choice2 < 0.05, na.rm = TRUE),
    significant_combined = sum(binom_p_value_combined < 0.05, na.rm = TRUE),
    total_participants = n(),
    mean_accuracy_choice1 = mean(percentage_accuracy_choice1),
    sd_accuracy_choice1 = sd(percentage_accuracy_choice1),
    mean_accuracy_choice2 = mean(percentage_accuracy_choice2),
    sd_accuracy_choice2 = sd(percentage_accuracy_choice2),
    mean_accuracy_combined = mean(percentage_accuracy_combined),
    sd_accuracy_combined = sd(percentage_accuracy_combined)
  )

# Individual results
summary_df %>%
  select(participant.id_in_session, 
         percentage_accuracy_choice1, percentage_accuracy_choice2, percentage_accuracy_combined,
         binom_p_value_choice1, binom_p_value_choice2, binom_p_value_combined) %>%
  mutate(across(starts_with("percentage"), ~round(., 2)),
         across(starts_with("binom"), ~round(., 3)))

# Aggregate tests for all three categories
aggregate_test_choice1 <- binom.test(
  sum(summary_df$total_choice1_accuracy), 
  sum(summary_df$valid_trials_choice1), 
  p = 0.5
)

aggregate_test_choice2 <- binom.test(
  sum(summary_df$total_choice2_accuracy), 
  sum(summary_df$valid_trials_choice2), 
  p = 0.5
)

aggregate_test_combined <- binom.test(
  sum(summary_df$total_combined_accuracy), 
  sum(summary_df$total_valid_trials), 
  p = 0.5
)

# Print aggregate results
print("Aggregate results for Choice 1:")
print(aggregate_test_choice1)
print("Aggregate results for Choice 2:")
print(aggregate_test_choice2)
print("Aggregate results for Combined Choices:")
print(aggregate_test_combined)

# Create long format data for plotting
plot_data <- summary_df %>%
  select(participant.id_in_session, 
         Choice1 = percentage_accuracy_choice1,
         Choice2 = percentage_accuracy_choice2,
         Combined = percentage_accuracy_combined) %>%
  pivot_longer(cols = c(Choice1, Choice2, Combined),
               names_to = "choice_type",
               values_to = "accuracy")

# Calculate means for labels
means <- plot_data %>%
  group_by(choice_type) %>%
  summarise(mean_accuracy = mean(accuracy, na.rm = TRUE))

# Create the plot
ggplot(plot_data, aes(x = choice_type, y = accuracy)) +
  geom_violin(fill = "gray90", alpha = 0.5) +
  geom_hline(yintercept = 50, linetype = "dashed", color = "red", alpha = 0.7) +
  geom_jitter(width = 0.1, alpha = 0.6, size = 1.5) +
  geom_point(data = means, aes(y = mean_accuracy), 
             color = "red", size = 3) +
  geom_text(data = means, 
            aes(y = 110, label = sprintf("%.1f", mean_accuracy)),
            size = 4.5) +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    plot.margin = margin(1, 0.5, 0.5, 1, "cm")
  ) +
  labs(x = NULL,
       y = "Percentage Accuracy",
       title = NULL) +
  scale_y_continuous(limits = c(-5, 120))
```

# Check split of reaction times per trial per decision

```{r}
rm(list=ls())
# Read the combined data
data <- read_csv(here("data", "preprocessed", "otree", "sessions", "main_task_filtered_03_03_1200.csv"), show_col_types = FALSE)

# First set of histograms
par(mfrow=c(2,2))
hist(data$player.initial_choice_time[data$player.initial_choice_time <= 3], 
     main="Initial Choice Time", xlab="Time", col="skyblue", border="white")
hist(data$player.initial_bet_time[data$player.initial_bet_time <= 3], 
     main="Initial Bet Time", xlab="Time", col="lightgreen", border="white")
hist(data$player.second_choice_time[data$player.second_choice_time <= 3], 
     main="Second Choice Time", xlab="Time", col="salmon", border="white")
hist(data$player.second_bet_time[data$player.second_bet_time <= 3], 
     main="Second Bet Time", xlab="Time", col="purple", border="white")

# Calculate aggregated data
meanIC <- aggregate(player.initial_choice_time ~ group.trial_number, data=data, FUN=mean)
meanIB <- aggregate(player.initial_bet_time ~ group.trial_number, data=data, FUN=mean)
meanSC <- aggregate(player.second_choice_time ~ group.trial_number, data=data, FUN=mean)
meanSB <- aggregate(player.second_bet_time ~ group.trial_number, data=data, FUN=mean)
sumCC1 <- aggregate(player.computer_choice_one ~ group.trial_number, data=data, FUN=sum)
sumCC2 <- aggregate(player.computer_choice_two ~ group.trial_number, data=data, FUN=sum)
sumCB1 <- aggregate(player.computer_bet_one ~ group.trial_number, data=data, FUN=sum)
sumCB2 <- aggregate(player.computer_bet_two ~ group.trial_number, data=data, FUN=sum)

# Second set of plots (means by trial number)
par(mfrow=c(2,2))
plot(meanIC, type="l", main="Mean Initial Choice Time", 
     xlab="Trial Number", ylab="Mean Time", col="blue", lwd=2)
plot(meanIB, type="l", main="Mean Initial Bet Time", 
     xlab="Trial Number", ylab="Mean Time", col="green", lwd=2)
plot(meanSC, type="l", main="Mean Second Choice Time", 
     xlab="Trial Number", ylab="Mean Time", col="red", lwd=2)
plot(meanSB, type="l", main="Mean Second Bet Time", 
     xlab="Trial Number", ylab="Mean Time", col="orange", lwd=2)

# Third set of plots (sums by trial number)
par(mfrow=c(2,2))
plot(sumCC1, type="l", main="Sum of Computer Choice One", 
     xlab="Trial Number", ylab="Sum", col="purple", lwd=2)
plot(sumCC2, type="l", main="Sum of Computer Choice Two", 
     xlab="Trial Number", ylab="Sum", col="brown", lwd=2)
plot(sumCB1, type="l", main="Sum of Computer Bet One", 
     xlab="Trial Number", ylab="Sum", col="darkgreen", lwd=2)
plot(sumCB2, type="l", main="Sum of Computer Bet Two", 
     xlab="Trial Number", ylab="Sum", col="darkblue", lwd=2)


# Reset the plotting layout
par(mfrow=c(1,1))
```


# Justify data cleaning by plotting how many trials have manual choices/bets and how many are made by the computer
```{r, fig.width=6, fig.height=6}
rm(list=ls())

# Function to create and plot the counts summary for any dataset
create_manual_vs_computer_plot <- function(data, title) {
  # Select the columns of interest and reshape to long format
  counts_data <- data %>%
    select(
      player.computer_choice_one,
      player.computer_bet_one,
      player.computer_choice_two,
      player.computer_bet_two
    ) %>%
    rename(
      "Choice 1" = player.computer_choice_one,
      "Bet 1" = player.computer_bet_one,
      "Choice 2" = player.computer_choice_two,
      "Bet 2" = player.computer_bet_two
    ) %>%
    pivot_longer(
      cols = everything(),
      names_to = "variable",
      values_to = "code"
    ) %>%
    filter(!is.na(code)) %>%
    mutate(
      type = ifelse(code == 0, "Manual", "Computer"),
      variable = factor(variable, levels = c("Choice 1", "Bet 1", "Choice 2", "Bet 2"))
    )
  
  # Count occurrences
  counts_summary <- counts_data %>%
    count(variable, type) %>%
    group_by(variable) %>%
    mutate(percentage = n / sum(n) * 100) %>%
    ungroup() %>%
    # Make sure "Manual" comes before "Computer" in the plot
    mutate(type = factor(type, levels = c("Manual", "Computer")))
  
  # Create the faceted plot
  ggplot(counts_summary, aes(x = type, y = n, fill = type)) +
    geom_col(width = 0.7) +
    # Manual bars - text inside
    geom_text(data = subset(counts_summary, type == "Manual"),
              aes(label = sprintf("%d\n(%.1f%%)", n, percentage)), 
              position = position_stack(vjust = 0.5),
              size = 4) +
    # Computer bars - text above
    geom_text(data = subset(counts_summary, type == "Computer"),
              aes(label = sprintf("%d\n(%.1f%%)", n, percentage)), 
              vjust = -0.5,  # Places text above the bar
              size = 4) +
    facet_wrap(~ variable, nrow = 2, ncol = 2) +
    scale_fill_manual(values = c("Manual" = "skyblue", "Computer" = "salmon")) +
    labs(
      title = title,
      x = NULL,
      y = "Count",
      fill = "Type"
    ) +
    theme_minimal() +
    theme(
      axis.title = element_text(size = 14),
      axis.text = element_text(size = 12),
      strip.text = element_text(size = 14, face = "bold"),
      panel.spacing = unit(1, "lines"),
      # Add some more space at the top for the labels
      plot.margin = margin(t = 20, r = 10, b = 10, l = 10, unit = "pt")
    )
}

# Read the first dataset (filtered data)
data_filtered <- read_csv(here("data", "preprocessed", "otree", "sessions", "main_task_filtered_03_03_1200.csv"), 
                        show_col_types = FALSE)

# Read the second dataset (unfiltered data)
data_unfiltered <- read_csv(here("data", "preprocessed", "otree", "sessions", "single", "single_main_task_03_03_1200.csv"), show_col_types = FALSE)

# Create plot for filtered data
plot_filtered <- create_manual_vs_computer_plot(data_filtered, "Manual vs. Computer Choices and Bets (Filtered Data)")

# Create plot for unfiltered data
plot_unfiltered <- create_manual_vs_computer_plot(data_unfiltered, "Manual vs. Computer Choices and Bets (Unfiltered Data)")

# Display plots
print(plot_filtered)
print(plot_unfiltered)
```