---
title: "otree_data_preprocessing"
author: "Aamir Sohail"
date: "2025-02-06"
output: html_document
---

```{r setup, include=FALSE}

# Install packages only if they are not already installed
required_packages <- c("ggplot2", "tidyverse", "readr", "here", "ggstatsplot", "ggpubr", "rstatix", "ggh4x")
install_if_missing <- required_packages[!required_packages %in% installed.packages()]
if (length(install_if_missing) > 0) {
  install.packages(install_if_missing, quietly = TRUE)
}

# Load required libraries
library(tidyverse)
library(ggplot2)
library(readr)
library(here)
library(ggstatsplot)
library(ggpubr)
library(rstatix)
library(ggh4x)
library(patchwork)
```

# Re-organise participant ids across sessions
```{r}
rm(list=ls())

# Read in datasets from current session with many session data
submission_data <- read_csv(here("data", "raw", "otree", "session_16_1500_6_3_25", "orig_data", "submission_2025-03-06.csv"), show_col_types = FALSE)
main_data <- read_csv(here("data", "raw", "otree", "session_16_1500_6_3_25", "orig_data", "main_task_2025-03-06.csv"), show_col_types = FALSE)

# Determine session order automatically
all_sessions <- c(submission_data$session.code, main_data$session.code)
session_order <- unique(all_sessions)

# Create a lookup table for mapping session code and original ID to new ID
create_id_lookup <- function(submission_df, main_df, session_order) {
  # Extract unique combinations from both datasets
  submission_ids <- submission_df %>% 
    select(session.code, participant.id_in_session) %>% 
    distinct()
  
  main_ids <- main_df %>% 
    select(session.code, participant.id_in_session) %>% 
    distinct()
  
  # Combine and remove duplicates
  all_ids <- bind_rows(submission_ids, main_ids) %>% 
    distinct()
  
  # Create new IDs by session
  result <- data.frame(session.code = character(), 
                      original_id = numeric(), 
                      new_id = numeric())
  
  current_id <- 1
  for(session in session_order) {
    # Get participants for this session
    session_participants <- all_ids %>% 
      filter(session.code == session) %>% 
      arrange(participant.id_in_session)
    
    # Assign new IDs
    session_participants$new_id <- current_id:(current_id + nrow(session_participants) - 1)
    
    # Add to result
    result <- bind_rows(result, data.frame(
      session.code = session_participants$session.code, 
      original_id = session_participants$participant.id_in_session, 
      new_id = session_participants$new_id
    ))
    
    # Update current_id for next session
    current_id <- current_id + nrow(session_participants)
  }
  
  return(result)
}

# Create the lookup table
id_lookup <- create_id_lookup(submission_data, main_data, session_order)

# Update the participant IDs in both datasets
submission_data <- submission_data %>% 
  left_join(id_lookup, by = c("session.code" = "session.code", "participant.id_in_session" = "original_id")) %>% 
  mutate(participant.id_in_session = new_id) %>% 
  select(-new_id)

main_data <- main_data %>% 
  left_join(id_lookup, by = c("session.code" = "session.code", "participant.id_in_session" = "original_id")) %>% 
  mutate(participant.id_in_session = new_id) %>% 
  select(-new_id)

# Save the updated datasets
write_csv(submission_data, here("data", "raw", "otree", "session_16_1500_6_3_25", "submission_2025-03-06.csv"))
write_csv(main_data, here("data", "raw", "otree", "session_16_1500_6_3_25", "main_task_2025-03-06.csv"))
```


# Submission data checks (for feedback values)

First let's combine submission data for checks
```{r}
# Read the CSV files reflecting different sessions
data_s1 <- read_csv(here("data", "raw", "otree", "session_1_1200_20_2_25", "submission_2025-02-20.csv"), 
                    show_col_types = FALSE)
data_s2 <- read_csv(here("data", "raw", "otree", "session_2_1200_21_2_25", "submission_2025-02-21.csv"), 
                    show_col_types = FALSE)
data_s3 <- read_csv(here("data", "raw", "otree", "session_4_1200_27_2_25", "submission_2025-02-27.csv"), 
                    show_col_types = FALSE)
data_s4 <- read_csv(here("data", "raw", "otree", "session_11_1500_4_3_25", "submission_2025-03-04.csv"), 
                    show_col_types = FALSE)
data_s5 <- read_csv(here("data", "raw", "otree", "session_15_1200_6_3_25", "submission_2025-03-06.csv"), 
                    show_col_types = FALSE)
data_s6 <- read_csv(here("data", "raw", "otree", "session_16_1500_6_3_25", "submission_2025-03-06.csv"), 
                    show_col_types = FALSE)

# Get the maximum participant ID from data_s6 (now the base file)
max_id_s6 <- max(data_s6$participant.id_in_session)

# Adjust the participant IDs in data_s5
data_s5_adjusted <- data_s5 %>%
  mutate(participant.id_in_session = participant.id_in_session + max_id_s6)

# Get the maximum participant ID from adjusted data_s5
max_id_s5_adjusted <- max(data_s5_adjusted$participant.id_in_session)

# Adjust the participant IDs in data_s4
data_s4_adjusted <- data_s4 %>%
  mutate(participant.id_in_session = participant.id_in_session + max_id_s5_adjusted)

# Get the maximum participant ID from adjusted data_s4
max_id_s4_adjusted <- max(data_s4_adjusted$participant.id_in_session)

# Adjust the participant IDs in data_s3
data_s3_adjusted <- data_s3 %>%
  mutate(participant.id_in_session = participant.id_in_session + max_id_s4_adjusted)

# Get the maximum participant ID from adjusted data_s3
max_id_s3_adjusted <- max(data_s3_adjusted$participant.id_in_session)

# Adjust the participant IDs in data_s2
data_s2_adjusted <- data_s2 %>%
  mutate(participant.id_in_session = participant.id_in_session + max_id_s3_adjusted)

# Get the maximum participant ID from adjusted data_s2
max_id_s2_adjusted <- max(data_s2_adjusted$participant.id_in_session)

# Adjust the participant IDs in data_s1
data_s1_adjusted <- data_s1 %>%
  mutate(participant.id_in_session = participant.id_in_session + max_id_s2_adjusted)

# Bind the datasets and select specific columns
combined_data <- bind_rows(data_s6, data_s5_adjusted, data_s4_adjusted, data_s3_adjusted, data_s2_adjusted, data_s1_adjusted) %>%
  # Filter for non-NA main_task_bonus
  filter(!is.na(player.main_task_bonus)) %>%
  # Select specific columns
  select(participant.id_in_session,
         participant.code,
         participant.label,
         player.id_in_group,
         player.main_task_bonus,
         player.task_understanding,
         player.task_difficulty,
         player.engagement,
         player.influence,
         player.real_players,
         player.attention_focus,
         player.main_task_group_id,
         player.choice1_sum_earnings,
         player.choice2_sum_earnings,
         player.choice1_accuracy_sum,
         player.choice2_accuracy_sum,
         player.choice1_reward_binary_sum,
         player.choice2_reward_binary_sum,
         session.code)

# Save the combined dataset
write_csv(combined_data, 
          here("data", "preprocessed", "otree", "sessions", "combined_submissions.csv"))
```

And let's plot the feedback values from the submission data
```{r}
rm(list=ls())

combined_data <- read_csv(here("data", "preprocessed", "otree", "sessions", "combined_submissions.csv"), show_col_types = FALSE)

# Number of participants who completed the task (no filtering)
unique_participants_count <- n_distinct(combined_data$participant.label)

# Reshape the combined_data to long format
long_data <- combined_data %>%
  select(player.task_understanding, 
         player.task_difficulty, 
         player.engagement, 
         player.influence, 
         player.real_players, 
         player.attention_focus) %>%
  pivot_longer(cols = everything(),
               names_to = "measure",
               values_to = "score") %>%
  mutate(measure = str_remove(measure, "player."))

# Calculate means
means <- long_data %>%
  group_by(measure) %>%
  summarise(mean_score = mean(score, na.rm = TRUE))

# Create the plot
ggplot(long_data, aes(x = measure, y = score)) +
  geom_violin(fill = "gray90", alpha = 0.5) +
  geom_point(data = means, aes(y = mean_score), 
             color = "red", size = 3) +
  geom_text(data = means, 
            aes(y = 110, label = sprintf("%.1f", mean_score)),  # Fixed position at y=110
            size = 4.5) +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    plot.margin = margin(1, 0.5, 0.5, 1, "cm")
  ) +
  labs(x = NULL,
       y = "Score",
       title = NULL) +
  scale_y_continuous(limits = c(-5, 120))  # Increased to make room for labels at 110
```

# Main task data preprocessing

# Remove the first trial from data with 65 trials
```{r}
rm(list=ls())

# Define a function to process each file to avoid code duplication
process_main_task_data <- function(session_path, file_date) {
  # Read the CSV
  data <- read_csv(here("data", "raw", "otree", session_path, paste0("main_task_", file_date, ".csv")), 
                   show_col_types = FALSE)
  
  # Filter and modify
  data <- data %>%
    filter(group.trial_number != 1) %>%
    mutate(
      group.trial_number = group.trial_number - 1,
      subsession.round_number = subsession.round_number - 1
    )
  
  # Verify it's still a data frame
  if (!is.data.frame(data)) {
    stop("Data is not a data frame")
  }
  
  # Save the preprocessed data
  write_csv(data, here("data", "raw", "otree", session_path, 
                       paste0("main_task_", file_date, "_64trials.csv")))
  
  # Return success message
  return(paste("Processed", session_path, "successfully"))
}

# Process each file
process_main_task_data("session_11_1500_4_3_25", "2025-03-04")
process_main_task_data("session_15_1200_6_3_25", "2025-03-06")
process_main_task_data("session_16_1500_6_3_25", "2025-03-06")
```

Now let's combine the main task data
```{r}
rm(list=ls())

# Read the CSV files
data_s1 <- read_csv(here("data", "raw", "otree", "session_1_1200_20_2_25", "main_task_2025-02-20.csv"), 
                   show_col_types = FALSE)
data_s2 <- read_csv(here("data", "raw", "otree", "session_2_1200_21_2_25", "main_task_2025-02-21.csv"), 
                show_col_types = FALSE)
data_s3 <- read_csv(here("data", "raw", "otree", "session_4_1200_27_2_25", "main_task_2025-02-27_64trials.csv"), 
                show_col_types = FALSE)
data_s4 <- read_csv(here("data", "raw", "otree", "session_11_1500_4_3_25", "main_task_2025-03-04_64trials.csv"), 
                show_col_types = FALSE)
data_s5 <- read_csv(here("data", "raw", "otree", "session_15_1200_6_3_25", "main_task_2025-03-06_64trials.csv"), 
                show_col_types = FALSE)
data_s6 <- read_csv(here("data", "raw", "otree", "session_16_1500_6_3_25", "main_task_2025-03-06_64trials.csv"), 
                show_col_types = FALSE)

# Get the maximum participant ID from data_s6 (base file)
max_id_s6 <- max(data_s6$participant.id_in_session)

# Adjust the participant IDs in data_s5
data_s5_adjusted <- data_s5 %>%
  mutate(participant.id_in_session = participant.id_in_session + max_id_s6)

# Get the maximum participant ID from adjusted data_s5
max_id_s5_adjusted <- max(data_s5_adjusted$participant.id_in_session)

# Adjust the participant IDs in data_s4
data_s4_adjusted <- data_s4 %>%
  mutate(participant.id_in_session = participant.id_in_session + max_id_s5_adjusted)

# Get the maximum participant ID from adjusted data_s4
max_id_s4_adjusted <- max(data_s4_adjusted$participant.id_in_session)

# Adjust the participant IDs in data_s3
data_s3_adjusted <- data_s3 %>%
  mutate(participant.id_in_session = participant.id_in_session + max_id_s4_adjusted)

# Get the maximum participant ID from adjusted data_s3
max_id_s3_adjusted <- max(data_s3_adjusted$participant.id_in_session)

# Adjust the participant IDs in data_s2
data_s2_adjusted <- data_s2 %>%
  mutate(participant.id_in_session = participant.id_in_session + max_id_s3_adjusted)

# Get the maximum participant ID from adjusted data_s2
max_id_s2_adjusted <- max(data_s2_adjusted$participant.id_in_session)

# Adjust the participant IDs in data_s1
data_s1_adjusted <- data_s1 %>%
  mutate(participant.id_in_session = participant.id_in_session + max_id_s2_adjusted)

# Bind the datasets
# This will automatically fill missing columns with NA
combined_data <- bind_rows(data_s6, data_s5_adjusted, data_s4_adjusted, data_s3_adjusted, data_s2_adjusted, data_s1_adjusted)

# Save the combined dataset
write_csv(combined_data, 
         here("data", "preprocessed", "otree", "sessions", "combined_main_task.csv"))
```

Subset the main task data by removing unneeded columns and converting rewards to -1 and 1
```{r}
rm(list=ls())

# Read the CSV file
data <- read_csv(here("data", "preprocessed", "otree", "sessions", "combined_main_task.csv"), show_col_types = FALSE)

# Remove unneeded columns
data <- data[, !(names(data) %in% c(
  "participant._is_bot", "participant._index_in_pages", "player.last_check_time",
  "participant._max_page_index", "participant._current_app_name", 
  "participant._current_page_name", "participant.time_started_utc",
  "participant.visited", "participant.mturk_worker_id",
  "participant.mturk_assignment_id", "participant.payoff",
  "player.role", "player.payoff", "player.consecutive_missed_checks",
  "player.individual_page_load_time", "player.base_payoff",
  "player.manual_second_choice", "player.disconnection_streak",
  "player.is_bot", "player.last_connection_time", "player.last_check_time",
  "group.current_round", "group.second_bet_timer_ended_executed",
  "group.next_round_transition_time", "group.reversal_rounds",
  "group.bet_container_displayed", "group.remaining_images_displayed",
  "group.round_reward_set", "group.intertrial_interval", "group.all_players_loaded",
  "group.players_loaded_count", "group.disconnected_players",
  "group.bot_players", "group.active_bots",
  "group.disconnection_streaks",
  "session.label", "session.mturk_HITId",
  "session.mturk_HITGroupId", "session.comment",
  "session.is_demo"
))]


# Convert rewards to -1 and 1 instead of 0 and 1
data$player.trial_reward[data$player.trial_reward == 0] <- -1
data$player.loss_or_gain[data$player.loss_or_gain == 0] <- -1
data$player.player1_loss_or_gain[data$player.player1_loss_or_gain == 0] <- -1
data$player.player2_loss_or_gain[data$player.player2_loss_or_gain == 0] <- -1
data$player.player3_loss_or_gain[data$player.player3_loss_or_gain == 0] <- -1
data$player.player4_loss_or_gain[data$player.player4_loss_or_gain == 0] <- -1
```

Convert choice with/against to decimals instead of raw numbers
```{r}
# Convert choice with/against to decimals instead of raw numbers
# Create a function to apply the division
divide_by_4 <- function(x) {
  ifelse(x == 0, 0, x/4)
}

# Apply the transformation to each column
data$player.choice1_with <- divide_by_4(data$player.choice1_with)
data$player.choice1_against <- divide_by_4(data$player.choice1_against)
data$player.choice2_with <- divide_by_4(data$player.choice2_with)
data$player.choice2_against <- divide_by_4(data$player.choice2_against)

# Change the values of the group.reward_probabilty_A and group.reward_probabilty_B columns from 0.7 to 0.75 and from 0.3 to 0.25
data$group.reward_probability_A[data$group.reward_probability_A == 0.7] <- 0.75
data$group.reward_probability_B[data$group.reward_probability_B == 0.3] <- 0.25

# Rename group.thirty_percent_image to group.low_percent_image and group.seventy_percent_image to group.high_percent_image
data <- data %>%
  rename(group.low_percent_image = group.thirty_percent_image,
         group.high_percent_image = group.seventy_percent_image)
```

Remove trials where the player left and list the number of trials per participant
```{r}
# Remove trials where the player left
data <- data %>% 
  filter(!is.na(player.my_page_load_time))

# List the number of trials per participant
data %>%
  count(participant.id_in_session) %>%
  arrange(participant.id_in_session)
```

Remove participants with too few trials
```{r}
# Remove participants with too few trials
data <- data %>%
  group_by(participant.id_in_session) %>%
  filter(n() >= 59) %>%
  ungroup()

# List the number of trials per participant after filtering
data %>%
  count(participant.id_in_session) %>%
  arrange(participant.id_in_session)
```


Save the preprocessed data
```{r}
# Save the preprocessed data (remove pilots if not a pilot)
write_csv(data, here("data", "preprocessed", "otree", "sessions", "combined_main_task.csv"))
```

# Main task data checks and exclusions 

Load in the data
```{r}
rm(list=ls())

data <- read_csv(here("data", "preprocessed", "otree", "sessions", "combined_main_task.csv"), show_col_types = FALSE)
```


Run several checks, including:

Check the number of manual responses per participant (choices and bets)
Check the total number of trials where all choices and bets were made manually
Check the number of times image A and image B was selected manually
Check the average manual bet 1 and bet 2

```{r}
summary_df <- data %>%
  group_by(participant.id_in_session, participant.label) %>%
  summarise(
    sum_choice_one = sum(player.computer_choice_one, na.rm = TRUE),
    sum_choice_two = sum(player.computer_choice_two, na.rm = TRUE),
    sum_bet_one = sum(player.computer_bet_one, na.rm = TRUE),
    sum_bet_two = sum(player.computer_bet_two, na.rm = TRUE),
    
    # Separate counts for manual trials of each type
    manual_choice_one_trials = sum(player.computer_choice_one == 0, na.rm = TRUE),
    manual_choice_two_trials = sum(player.computer_choice_two == 0, na.rm = TRUE),
    manual_bet_one_trials = sum(player.computer_bet_one == 0, na.rm = TRUE),
    manual_bet_two_trials = sum(player.computer_bet_two == 0, na.rm = TRUE),
    
    # Count trials where computer_choice is 0
    count_choice_one_zero = sum(player.computer_choice_one == 0, na.rm = TRUE),
    count_choice_two_zero = sum(player.computer_choice_two == 0, na.rm = TRUE),
    
    # Count 1s and 2s only when respective computer_choice is 0
    count_ones_image_one = sum(player.chosen_image_one_binary == '1' & 
                              player.computer_choice_one == 0, na.rm = TRUE),
    count_twos_image_one = sum(player.chosen_image_one_binary == '2' & 
                              player.computer_choice_one == 0, na.rm = TRUE),
    count_ones_image_two = sum(player.chosen_image_two_binary == '1' & 
                              player.computer_choice_two == 0, na.rm = TRUE),
    count_twos_image_two = sum(player.chosen_image_two_binary == '2' & 
                              player.computer_choice_two == 0, na.rm = TRUE),
    
    # Average bets when computer bets are 0
    avg_bet_one = mean(player.bet1[player.computer_bet_one == 0], na.rm = TRUE),
    avg_bet_two = mean(player.bet2[player.computer_bet_two == 0], na.rm = TRUE)
  )

# Create separate dataframes for each type of response with too few manual trials
low_choice_one_participants <- summary_df %>%
  filter(manual_choice_one_trials < 45) %>%
  select(participant.id_in_session, participant.label, manual_choice_one_trials) %>%
  mutate(Reason = "Too few manual choice one trials")

low_choice_two_participants <- summary_df %>%
  filter(manual_choice_two_trials < 45) %>%
  select(participant.id_in_session, participant.label, manual_choice_two_trials) %>%
  mutate(Reason = "Too few manual choice two trials")

low_bet_one_participants <- summary_df %>%
  filter(manual_bet_one_trials < 45) %>%
  select(participant.id_in_session, participant.label, manual_bet_one_trials) %>%
  mutate(Reason = "Too few manual bet one trials")

low_bet_two_participants <- summary_df %>%
  filter(manual_bet_two_trials < 45) %>%
  select(participant.id_in_session, participant.label, manual_bet_two_trials) %>%
  mutate(Reason = "Too few manual bet two trials")

# Print results for each type
cat("Participants with fewer than 45 manual choice one trials:\n")
print(low_choice_one_participants)
cat("\nParticipants with fewer than 45 manual choice two trials:\n")
print(low_choice_two_participants)
cat("\nParticipants with fewer than 45 manual bet one trials:\n")
print(low_bet_one_participants)
cat("\nParticipants with fewer than 45 manual bet two trials:\n")
print(low_bet_two_participants)

# Combine participants who have too few trials in either choice one or choice two
combined_low_choices <- bind_rows(low_choice_one_participants, low_choice_two_participants, low_bet_one_participants, low_bet_two_participants) %>%
  distinct(participant.id_in_session, .keep_all = TRUE)

# Save to CSV
write.csv(combined_low_choices,
          file = "excluded_otree_subjects.csv",
          row.names = FALSE)

cat("Number of participants excluded:", nrow(combined_low_choices))
```

Get the participants with too many choices of the same image (over 75% or under 25%)
```{r}
# First read existing data
if(file.exists("excluded_otree_subjects.csv")) {
  existing_data <- read.csv("excluded_otree_subjects.csv")
} else {
  existing_data <- data.frame()
}

# Remove players who choose the same image more than 75% of the time or less than 25% of the time
high_ones_participants <- summary_df %>%
  filter(count_ones_image_one > 48 | count_ones_image_one < 16) %>%
  select(participant.id_in_session, participant.label, count_ones_image_one) %>%
  mutate(
    manual_choice_one_trials = NA,
    Reason = "Too many/few choices of the same image",
    manual_choice_two_trials = NA
  )

# Print to console
cat("Participants with count_ones_image_one above 50:\n")
print(high_ones_participants)

# Combine and write back to CSV
combined_data <- bind_rows(existing_data, high_ones_participants)
write.csv(combined_data, 
          file = "excluded_otree_subjects.csv",
          row.names = FALSE)
```


Remove participants with too few manual trials and too many choices of the same image

```{r}
# Read the CSV with excluded participants
excluded_participants <- read.csv("excluded_otree_subjects.csv") %>%
  distinct(participant.label)  # Get unique participant labels

# Filter out these participants from the main data
filtered_data <- data %>%
  filter(!participant.label %in% excluded_participants$participant.label)

# Print how many participants were excluded
cat("Number of participants excluded:", nrow(excluded_participants), "\n")

write_csv(filtered_data, here("data", "preprocessed", "otree", "sessions", "main_task_combined_filtered.csv"))
```


# Remove participants who completed the task twice 

```{r}
rm(list=ls())

# Load the filtered data
data <- read_csv(here("data", "preprocessed", "otree", "sessions", "main_task_combined_filtered.csv"), show_col_types = FALSE)

# Remove rows that match both conditions
data <- data %>%
  filter(!(participant.label == "666f1aec64844fbd48cd89b8" & participant.code == "xau7lc95"))

# Save the filtered data back to the same file
write_csv(data, here("data", "preprocessed", "otree", "sessions", "main_task_combined_filtered.csv"))

# Reload the data from the saved file
data <- read_csv(here("data", "preprocessed", "otree", "sessions", "main_task_combined_filtered.csv"), show_col_types = FALSE)
```


# Perform basic checks and visualizations of the cleaned oTree data

# Plot filtered submission data - only include those who are included in the main task
```{r}
rm(list=ls())

data <- read_csv(here("data", "preprocessed", "otree", "sessions", "main_task_combined_filtered.csv"), show_col_types = FALSE)

# Load in submission data 
submission_data <- read_csv(here("data", "preprocessed", "otree", "sessions", "combined_submissions.csv"), show_col_types = FALSE)

# Get unique participant labels from data
valid_participants <- unique(data$participant.label)

# Filter submission_data to only include rows with valid participant labels
filtered_submission_data <- submission_data %>%
  filter(participant.label %in% valid_participants)

# Save the filtered data
write_csv(filtered_submission_data, here("data", "preprocessed", "otree", "sessions", "combined_filtered_submissions.csv"))
```


# Various checks and visualizations - re-plot feedback, plot histograms of score/performance

```{r, fig.width=10, fig.height=10}
# First plot: Violin plot of survey measures
long_data <- filtered_submission_data %>%
  select(player.task_understanding, 
         player.task_difficulty, 
         player.engagement, 
         player.influence, 
         player.real_players, 
         player.attention_focus) %>%
  pivot_longer(cols = everything(),
               names_to = "measure",
               values_to = "score") %>%
  mutate(measure = str_remove(measure, "player."))

# Calculate means
means <- long_data %>%
  group_by(measure) %>%
  summarise(mean_score = mean(score, na.rm = TRUE))

# Create the violin plot
violin_plot <- ggplot(long_data, aes(x = measure, y = score)) +
  geom_violin(fill = "gray90", alpha = 0.5) +
  geom_point(data = means, aes(y = mean_score), 
             color = "red", size = 3) +
  geom_text(data = means, 
            aes(y = 110, label = sprintf("%.1f", mean_score)),
            size = 4.5) +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    plot.margin = margin(1, 0.5, 0.5, 1, "cm")
  ) +
  labs(x = NULL,
       y = "Score",
       title = NULL) +
  scale_y_continuous(limits = c(-5, 120))

# Filter out people with player.choice1_accuracy_sum < 10 for the histogram facet plots
filtered_choices_data <- filtered_submission_data %>%
  filter(player.choice1_accuracy_sum >= 10)

# Create the long format data for the histograms
long_choices <- filtered_choices_data %>%
  select(player.choice1_sum_earnings, 
         player.choice2_sum_earnings,
         player.choice1_accuracy_sum,
         player.choice2_accuracy_sum,
         player.choice1_reward_binary_sum,
         player.choice2_reward_binary_sum) %>%
  pivot_longer(cols = everything(),
               names_to = "metric",
               values_to = "value") %>%
  mutate(
    choice = case_when(
      str_detect(metric, "choice1") ~ "Choice 1",
      str_detect(metric, "choice2") ~ "Choice 2",
      TRUE ~ NA_character_
    ),
    measure_type = case_when(
      str_detect(metric, "earnings") ~ "Earnings",
      str_detect(metric, "accuracy") ~ "Accuracy",
      str_detect(metric, "reward_binary") ~ "Reward Binary",
      TRUE ~ NA_character_
    )
  )

# Calculate means for each group
means_data <- long_choices %>%
  group_by(choice, measure_type) %>%
  summarize(mean_value = mean(value, na.rm = TRUE), .groups = "drop")

# Create separate plots for each measure type
# 1. Accuracy plot
p1 <- ggplot(long_choices %>% filter(measure_type == "Accuracy"), 
            aes(x = value)) +
  geom_histogram(fill = "steelblue", color = "black", alpha = 0.7, bins = 30) +
  geom_vline(data = means_data %>% filter(measure_type == "Accuracy"),
            aes(xintercept = mean_value), 
            linetype = "dashed", color = "red", size = 1) +
  geom_text(data = means_data %>% filter(measure_type == "Accuracy"),
           aes(x = mean_value + 5, y = Inf, 
               label = sprintf("%.1f", mean_value)),
           vjust = 2, color = "red") +
  facet_grid(. ~ choice) +
  theme_classic() +
  labs(x = "Value", y = "Count", title = "Accuracy") +
  theme(strip.text = element_text(size = 12),
        plot.title = element_text(hjust = 1))

# 2. Earnings plot
p2 <- ggplot(long_choices %>% filter(measure_type == "Earnings"), 
            aes(x = value)) +
  geom_histogram(fill = "steelblue", color = "black", alpha = 0.7, bins = 30) +
  geom_vline(data = means_data %>% filter(measure_type == "Earnings"),
            aes(xintercept = mean_value), 
            linetype = "dashed", color = "red", size = 1) +
  geom_text(data = means_data %>% filter(measure_type == "Earnings"),
           aes(x = mean_value + 50, y = Inf, 
               label = sprintf("%.1f", mean_value)),
           vjust = 2, color = "red") +
  facet_grid(. ~ choice) +
  theme_classic() +
  labs(x = "Value", y = "Count", title = "Earnings") +
  theme(strip.text = element_text(size = 12),
        plot.title = element_text(hjust = 1))

# 3. Reward Binary plot
p3 <- ggplot(long_choices %>% filter(measure_type == "Reward Binary"), 
            aes(x = value)) +
  geom_histogram(fill = "steelblue", color = "black", alpha = 0.7, bins = 30) +
  geom_vline(data = means_data %>% filter(measure_type == "Reward Binary"),
            aes(xintercept = mean_value), 
            linetype = "dashed", color = "red", size = 1) +
  geom_text(data = means_data %>% filter(measure_type == "Reward Binary"),
           aes(x = mean_value + 5, y = Inf, 
               label = sprintf("%.1f", mean_value)),
           vjust = 2, color = "red") +
  facet_grid(. ~ choice) +
  theme_classic() +
  labs(x = "Value", y = "Count", title = "Reward Binary") +
  theme(strip.text = element_text(size = 12),
        plot.title = element_text(hjust = 1))

# Combine the histogram plots vertically with the patchwork package
histograms_combined <- p1 / p2 / p3

# Display the plots
violin_plot
histograms_combined
```

# count number of complete participants in groups - compare between filtered and unfiltered sample

```{r}
# Load the combined data
combined_data <- read_csv(here("data", "preprocessed", "otree", "sessions", "combined_submissions.csv"), show_col_types = FALSE)

# Calculate the group sizes and distribution for filtered_submission_data
filtered_group_counts <- filtered_submission_data %>%
  # Count how many participants have the same group ID within each session
  group_by(session.code, player.main_task_group_id) %>%
  summarise(members_per_group = n(), .groups = "drop") %>%
  # Count how many groups of each size exist across all sessions
  group_by(members_per_group) %>%
  summarise(count = n(), .groups = "drop")

# Create the histogram for filtered_submission_data
p1 <- ggplot(filtered_group_counts, aes(x = as.factor(members_per_group), y = count)) +
  geom_bar(stat = "identity", fill = "steelblue", alpha = 0.7) +
  geom_text(aes(label = count), vjust = -0.5, size = 4.5) +
  theme_classic() +
  labs(
    x = "Number of Participants in Group",
    y = "Count of Groups",
    title = "Distribution of Group Sizes (Filtered Data)"
  ) +
  theme(
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 14),
    plot.title = element_text(hjust = 0.5, size = 16)
  )

# Calculate the group sizes and distribution for combined_data
combined_group_counts <- combined_data %>%
  # Count how many participants have the same group ID within each session
  group_by(session.code, player.main_task_group_id) %>%
  summarise(members_per_group = n(), .groups = "drop") %>%
  # Count how many groups of each size exist across all sessions
  group_by(members_per_group) %>%
  summarise(count = n(), .groups = "drop")

# Create the histogram for combined_data
p2 <- ggplot(combined_group_counts, aes(x = as.factor(members_per_group), y = count)) +
  geom_bar(stat = "identity", fill = "steelblue", alpha = 0.7) +
  geom_text(aes(label = count), vjust = -0.5, size = 4.5) +
  theme_classic() +
  labs(
    x = "Number of Participants in Group",
    y = "Count of Groups",
    title = "Distribution of Group Sizes (All Data)"
  ) +
  theme(
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 14),
    plot.title = element_text(hjust = 0.5, size = 16)
  )

# Display both plots
p1
p2
```

Re-calculate the checks from before:

- Check the number of manual responses per participant (choices and bets)
- Check the total number of trials where all choices and bets were made manually
- Check the number of times image A and image B was selected manually
- Check the average manual bet 1 and bet 2

```{r}
rm(list=ls())

data <- read_csv(here("data", "preprocessed", "otree", "sessions", "main_task_combined_filtered.csv"), show_col_types = FALSE)

summary_df <- data %>%
  group_by(participant.id_in_session, participant.label) %>%
  summarise(
    sum_choice_one = sum(player.computer_choice_one, na.rm = TRUE),
    sum_choice_two = sum(player.computer_choice_two, na.rm = TRUE),
    sum_bet_one = sum(player.computer_bet_one, na.rm = TRUE),
    sum_bet_two = sum(player.computer_bet_two, na.rm = TRUE),
    
    # Separate counts for manual trials of each type
    manual_choice_one_trials = sum(player.computer_choice_one == 0, na.rm = TRUE),
    manual_choice_two_trials = sum(player.computer_choice_two == 0, na.rm = TRUE),
    manual_bet_one_trials = sum(player.computer_bet_one == 0, na.rm = TRUE),
    manual_bet_two_trials = sum(player.computer_bet_two == 0, na.rm = TRUE),
    
    # Count trials where computer_choice is 0
    count_choice_one_zero = sum(player.computer_choice_one == 0, na.rm = TRUE),
    count_choice_two_zero = sum(player.computer_choice_two == 0, na.rm = TRUE),
    
    # Count 1s and 2s only when respective computer_choice is 0
    count_ones_image_one = sum(player.chosen_image_one_binary == '1' & 
                              player.computer_choice_one == 0, na.rm = TRUE),
    count_twos_image_one = sum(player.chosen_image_one_binary == '2' & 
                              player.computer_choice_one == 0, na.rm = TRUE),
    count_ones_image_two = sum(player.chosen_image_two_binary == '1' & 
                              player.computer_choice_two == 0, na.rm = TRUE),
    count_twos_image_two = sum(player.chosen_image_two_binary == '2' & 
                              player.computer_choice_two == 0, na.rm = TRUE),
    
    # Average bets when computer bets are 0
    avg_bet_one = mean(player.bet1[player.computer_bet_one == 0], na.rm = TRUE),
    avg_bet_two = mean(player.bet2[player.computer_bet_two == 0], na.rm = TRUE)
  )

# Calculate group averages
group_averages <- summary_df %>%
  summarise(
    avg_manual_choice_one = mean(manual_choice_one_trials, na.rm = TRUE),
    avg_manual_choice_two = mean(manual_choice_two_trials, na.rm = TRUE),
    avg_manual_bet_one = mean(manual_bet_one_trials, na.rm = TRUE),
    avg_manual_bet_two = mean(manual_bet_two_trials, na.rm = TRUE)
  )

# Reshape the data to long format for plotting
plot_data <- summary_df %>%
  select(participant.id_in_session, 
         manual_choice_one_trials, 
         manual_choice_two_trials, 
         manual_bet_one_trials, 
         manual_bet_two_trials) %>%
  pivot_longer(cols = starts_with("manual"),
               names_to = "response_type",
               values_to = "count") %>%
  mutate(response_type = factor(response_type,
                               levels = c("manual_choice_one_trials",
                                        "manual_choice_two_trials",
                                        "manual_bet_one_trials",
                                        "manual_bet_two_trials"),
                               labels = c("Choice 1",
                                        "Choice 2",
                                        "Bet 1",
                                        "Bet 2")))

# Calculate means for each response type
means_data <- plot_data %>%
  group_by(response_type) %>%
  summarise(mean_count = mean(count, na.rm = TRUE))

# Create the violin plot with means
ggplot(plot_data, aes(x = response_type, y = count)) +
  geom_violin(fill = "lightblue", alpha = 0.5) +
  geom_boxplot(width = 0.1, alpha = 0.2, outlier.shape = NA) +
  geom_text(data = means_data, 
            aes(y = max(plot_data$count, na.rm = TRUE) * 1.05, 
                label = sprintf("%.2f", mean_count)),
            vjust = 0) +
  theme_minimal() +
  labs(x = "Response Type",
       y = "Number of Manual Responses",
       title = "Distribution of Manual Responses by Type") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Plot the number of time image 1 was chosen manually, and the average bet sizes
```{r}
# Reshape data for the count_ones plot
counts_data <- summary_df %>%
  select(participant.id_in_session, count_ones_image_one, count_ones_image_two) %>%
  pivot_longer(cols = c(count_ones_image_one, count_ones_image_two),
               names_to = "choice_type",
               values_to = "count")

# Rest of your original code...
bets_data <- summary_df %>%
  select(participant.id_in_session, avg_bet_one, avg_bet_two) %>%
  pivot_longer(cols = c(avg_bet_one, avg_bet_two),
               names_to = "bet_type",
               values_to = "average_bet")

# Create violin plot for count_ones
count_plot <- ggbetweenstats(
  data = counts_data,
  x = choice_type,
  y = count,
  title = "Distribution of '1' Choices by Image Type",
  xlab = "Choice Type",
  ylab = "Count of '1' Choices",
  type = "nonparametric",
  package = "ggsci",
  palette = "nrc_npg",
  messages = FALSE
)

# Create violin plot for average bets
bets_plot <- ggbetweenstats(
  data = bets_data,
  x = bet_type,
  y = average_bet,
  title = "Distribution of Average Bets",
  xlab = "Bet Type",
  ylab = "Average Bet",
  type = "nonparametric",
  package = "ggsci",
  palette = "nrc_npg",
  messages = FALSE
)

# Display plots
count_plot
bets_plot
```

Calculate and plot the proportion of each image chosen for each block for both choices, and the accuracy
Ideally, you would expect for the proportion of each image chosen to be around 0.6-0.7 for each block
```{r}
# Function to process data and create plots and tables
analyze_choices <- function(data, choice_column, computer_column, prop_title) {
  # Calculate proportions, counts, and accuracy
  participant_blocks <- data %>%
    filter(!!sym(computer_column) == 0) %>%
    mutate(block = case_when(
      subsession.round_number <= 15 ~ "1-15",
      subsession.round_number <= 32 ~ "16-32",
      subsession.round_number <= 47 ~ "33-47",
      TRUE ~ "48-64"
    )) %>%
    group_by(participant.id_in_session, block) %>%
    summarize(
      ones_count = sum(!!sym(choice_column) == 1),
      twos_count = sum(!!sym(choice_column) == 2),
      total_trials = n(),
      prop_ones = mean(!!sym(choice_column) == 1),
      prop_twos = mean(!!sym(choice_column) == 2),
      .groups = 'drop'
    ) %>%
    mutate(
      ones_fraction = sprintf("%d/%d", ones_count, total_trials),
      twos_fraction = sprintf("%d/%d", twos_count, total_trials),
      accuracy = case_when(
        block %in% c("1-15", "33-47") ~ prop_ones,
        block %in% c("16-32", "48-64") ~ prop_twos
      )
    )
  
  # Create counts table
  counts_table <- participant_blocks %>%
    select(participant.id_in_session, block, ones_fraction, twos_fraction)
  
  # Create final dataset for choice plotting
  blocks_final <- participant_blocks %>%
    pivot_longer(
      cols = c(prop_ones, prop_twos),
      names_to = "choice",
      values_to = "proportion"
    )
  
  # Run paired t-tests for choices
  significance_tests <- blocks_final %>%
    group_by(block) %>%
    summarize(
      p_value = t.test(
        proportion[choice == "prop_ones"],
        proportion[choice == "prop_twos"],
        paired = TRUE
      )$p.value,
      significance = case_when(
        p_value < 0.001 ~ "***",
        p_value < 0.01 ~ "**",
        p_value < 0.05 ~ "*",
        TRUE ~ "ns"
      ),
      y_pos = max(proportion) + 0.1
    )
  
  # Create choice plot
  choice_plot <- ggplot(blocks_final, aes(x = block, y = proportion, color = choice)) +
    geom_jitter(width = 0.2, alpha = 0.5, size = 0.4) +
    stat_summary(fun = mean, geom = "point", size = 5) +
    stat_summary(fun = mean, geom = "line", aes(group = choice)) +
    geom_text(data = significance_tests, 
              aes(x = block, y = y_pos, label = significance),
              color = "black") +
    theme_minimal() +
    labs(
      title = prop_title,
      x = "Trial Block",
      y = "Proportion",
      color = "Choice"
    ) +
    scale_color_manual(
      values = c("prop_ones" = "blue", "prop_twos" = "red"),
      labels = c("prop_ones" = "Ones", "prop_twos" = "Twos")
    )
  
  return(list(plot = choice_plot, 
             data = participant_blocks,
             counts = counts_table))
}

# Function to process accuracy data
process_accuracy_data <- function(data, choice_column, computer_column, choice_label) {
  participant_blocks <- data %>%
    filter(!!sym(computer_column) == 0) %>%
    mutate(block = case_when(
      subsession.round_number <= 15 ~ "1-15",
      subsession.round_number <= 32 ~ "16-32",
      subsession.round_number <= 47 ~ "33-47",
      TRUE ~ "48-64"
    )) %>%
    group_by(participant.id_in_session, block) %>%
    summarize(
      ones_count = sum(!!sym(choice_column) == 1),
      twos_count = sum(!!sym(choice_column) == 2),
      total_trials = n(),
      prop_ones = mean(!!sym(choice_column) == 1),
      prop_twos = mean(!!sym(choice_column) == 2),
      .groups = 'drop'
    ) %>%
    mutate(
      accuracy = case_when(
        block %in% c("1-15", "33-47") ~ prop_ones,
        block %in% c("16-32", "48-64") ~ prop_twos
      ),
      choice_type = choice_label
    )
  
  return(participant_blocks)
}

# Run analyses for proportion plots
results_one <- analyze_choices(data, 
                             "player.chosen_image_one_binary", 
                             "player.computer_choice_one", 
                             "Proportion of 1's and 2's by Block (First Choice)")
results_two <- analyze_choices(data, 
                             "player.chosen_image_two_binary", 
                             "player.computer_choice_two", 
                             "Proportion of 1's and 2's by Block (Second Choice)")

# Process data for accuracy plot
accuracy_one <- process_accuracy_data(data, 
                                    "player.chosen_image_one_binary", 
                                    "player.computer_choice_one", 
                                    "First Choice")
accuracy_two <- process_accuracy_data(data, 
                                    "player.chosen_image_two_binary", 
                                    "player.computer_choice_two", 
                                    "Second Choice")

# Combine accuracy data
combined_accuracy <- rbind(accuracy_one, accuracy_two)

# Create combined accuracy plot
accuracy_plot <- ggplot(combined_accuracy, 
                       aes(x = block, y = accuracy, color = choice_type)) +
  geom_jitter(width = 0.2, alpha = 0.3, size = 0.8) +  
  stat_summary(fun = mean, geom = "point", size = 3) +  
  stat_summary(fun = mean, geom = "line", aes(group = choice_type), linewidth = 1) +
  theme_minimal() +
  labs(
    title = "Mean Accuracy by Block for Both Choices",
    x = "Trial Block",
    y = "Accuracy",
    color = "Choice"
  ) +
  scale_color_manual(values = c("First Choice" = "blue", "Second Choice" = "red"))

# Display plots
results_one$plot
results_two$plot
accuracy_plot

# Display tables
print("Counts for First Choice:")
print(results_one$counts)
print("Counts for Second Choice:")
print(results_two$counts)
```


Comparing accuracy to the 'ground truth'
```{r}
# Create a data frame for the red dots
dot_data <- data.frame(
  block = c("1-15", "16-32", "33-47", "48-64"),
  y_value = c(0.8, 0.765, 0.733, 0.706)
)

# Calculate mean accuracy per block for each choice type
mean_accuracy_by_block <- combined_accuracy %>%
  group_by(block, choice_type) %>%
  summarize(
    mean_accuracy = mean(accuracy, na.rm = TRUE),
    se = sd(accuracy, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )

# Calculate combined means across choice types
combined_means <- combined_accuracy %>%
  group_by(block) %>%
  summarize(
    combined_mean = mean(accuracy, na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  mutate(
    combined_mean_rounded = round(combined_mean, 1),
    combined_label = sprintf("%.2f", combined_mean)
  )

# Create bar chart of mean accuracy by block with the red dots
accuracy_bar_chart <- ggplot(mean_accuracy_by_block, 
                           aes(x = block, y = mean_accuracy, fill = choice_type)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9), width = 0.8) +
  coord_cartesian(ylim = c(0.5, 0.82)) +
  geom_errorbar(aes(ymin = mean_accuracy - se, ymax = mean_accuracy + se),
                position = position_dodge(width = 0.9), width = 0.25) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "red") +
  # Add the red dots
  geom_point(data = dot_data, mapping = aes(x = block, y = y_value), 
             inherit.aes = FALSE, color = "red", size = 3) +
  # Add labels below the red dots
  geom_text(data = dot_data, mapping = aes(x = block, y = y_value, 
            label = sprintf("%.2f", y_value)),
            inherit.aes = FALSE, vjust = 1.5, color = "red", fontface = "bold") +
  # Add combined mean labels at the bottom of the plot
  geom_text(data = combined_means, mapping = aes(x = block, y = 0.51, 
            label = combined_label),
            inherit.aes = FALSE, vjust = 0, color = "black", fontface = "bold") +
  theme_minimal() +
  labs(
    title = "Mean Accuracy by Block for Both Choices",
    x = "Trial Block",
    y = "Mean Accuracy",
    fill = "Choice"
  ) +
  scale_fill_manual(values = c("First Choice" = "skyblue", "Second Choice" = "coral")) +
  theme(
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12, face = "bold"),
    legend.position = "bottom"
  ) +
  scale_y_continuous(breaks = seq(0.5, 0.8, 0.1))

# Display the bar chart
accuracy_bar_chart
```


Reaction time for manual choices and bets
```{r}
# Calculate timing means with specific column order
timing_summary_df <- data %>%
  group_by(participant.id_in_session) %>%
  summarise(
    mean_initial_choice_time = mean(player.initial_choice_time[player.computer_choice_one == 0], na.rm = TRUE),
    mean_initial_bet_time = mean(player.initial_bet_time[player.computer_bet_one == 0], na.rm = TRUE),
    mean_second_choice_time = mean(player.second_choice_time[player.computer_choice_two == 0], na.rm = TRUE),
    mean_second_bet_time = mean(player.second_bet_time[player.computer_bet_two == 0], na.rm = TRUE)
  )

# Create a manual ordering vector
order_levels <- c("mean_initial_choice_time", 
                 "mean_initial_bet_time",
                 "mean_second_choice_time", 
                 "mean_second_bet_time")

nice_labels <- c("Initial Choice Time",
                "Initial Bet Time",
                "Second Choice Time",
                "Second Bet Time")

# Reshape data for plotting
timing_data <- timing_summary_df %>%
  pivot_longer(cols = -participant.id_in_session,
               names_to = "timing_type",
               values_to = "time") %>%
  mutate(timing_type = factor(timing_type, 
                             levels = order_levels,
                             labels = nice_labels))

# Create violin plot
ggbetweenstats(
  data = timing_data,
  x = timing_type,
  y = time,
  title = "Distribution of Response Times",
  xlab = "Response Type",
  ylab = "Time (seconds)",
  type = "nonparametric",
  package = "ggsci",
  palette = "nrc_npg",
  messages = FALSE
) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Reaction time for manual choices and bets across blocks

```{r}
# Create a function to process and plot reaction times
plot_reaction_times <- function(data, time_column, computer_column, title) {
  # Filter and prepare data
  rt_data <- data %>%
    filter(!!sym(computer_column) == 0) %>%
    filter(!!sym(time_column) <= 3) %>%  # Filter out trials > 3 seconds
    mutate(block = case_when(
      subsession.round_number <= 15 ~ "1-15",
      subsession.round_number <= 32 ~ "16-32",
      subsession.round_number <= 47 ~ "33-47",
      TRUE ~ "48-64"
    )) %>%
    # Calculate participant averages per block
    group_by(participant.id_in_session, block) %>%
    summarise(
      avg_rt = mean(!!sym(time_column), na.rm = TRUE)
    ) %>%
    ungroup() %>%
    # Convert block to factor to maintain order
    mutate(block = factor(block, levels = c("1-15", "16-32", "33-47", "48-64")))

  # Create violin plot using ggbetweenstats
  plot <- ggbetweenstats(
    data = rt_data,
    x = block,
    y = avg_rt,
    type = "nonparametric",
    plot.type = "violin",
    title = title,
    xlab = "Trial Block",
    ylab = "Average Response Time (seconds)",
    violin.args = list(width = 0.5, alpha = 0.4),
    point.args = list(
      alpha = 0.5, 
      size = 2,
      position = position_jitter(width = 0.2, seed = 123)  # Add more jitter
    ),
    results.subtitle = FALSE,
    pairwise.comparisons = FALSE
  )
  
  return(plot)
}

# Generate all four plots
initial_choice_plot <- plot_reaction_times(
  data,
  "player.initial_choice_time",
  "player.computer_choice_one",
  "Initial Choice Response Times by Block"
)
second_choice_plot <- plot_reaction_times(
  data,
  "player.second_choice_time",
  "player.computer_choice_two",
  "Second Choice Response Times by Block"
)
initial_bet_plot <- plot_reaction_times(
  data,
  "player.initial_bet_time",
  "player.computer_bet_one",
  "Initial Bet Response Times by Block"
)
second_bet_plot <- plot_reaction_times(
  data,
  "player.second_bet_time",
  "player.computer_bet_two",
  "Second Bet Response Times by Block"
)

# Display all plots
initial_choice_plot
second_choice_plot
initial_bet_plot
second_bet_plot
```

Cumulative earnings over trials from choice 2
```{r}
# First, calculate the mean score at the final round
final_round <- max(data$subsession.round_number)
final_mean_score <- data %>%
  filter(subsession.round_number == final_round) %>%
  summarise(mean_score = mean(player.choice2_sum_earnings, na.rm = TRUE)) %>%
  pull(mean_score)

# Now use this in the plot
ggplot() +
  # Individual participant lines with high transparency
  geom_line(data = data, 
            aes(x = subsession.round_number, 
                y = player.choice2_sum_earnings, 
                group = participant.id_in_session,
                color = factor(participant.id_in_session)),
            alpha = 0.2) +
  # Smoothed mean line with standard error
  geom_smooth(data = data,
             aes(x = subsession.round_number, y = player.choice2_sum_earnings),
             color = "blue",
             size = 1.5,
             se = TRUE,
             method = "loess") +
  # Vertical lines
  geom_vline(xintercept = 16, linetype = "dashed", color = "red") +
  geom_vline(xintercept = 33, linetype = "dashed", color = "red") +
  geom_vline(xintercept = 48, linetype = "dashed", color = "red") +
  # Add text annotation for mean score
  annotate("text", 
           x = final_round + 1,  # Position slightly to the right of final round
           y = final_mean_score,
           label = sprintf("%.1f", final_mean_score),
           hjust = 0,
           color = "blue",
           fontface = "bold",
           size = 6) +
  labs(title = "Cumulative Score Over Trials by Participant (Choice 2 Outcome)",
       subtitle = "Blue line shows smoothed mean score with standard error bands",
       x = "Trial Number",
       y = "Score") +
  theme_minimal() +
  theme(legend.position = "none",
        plot.margin = margin(r = 40, unit = "pt")) +  # Add right margin
  coord_cartesian(clip = "off")  # Allow drawing outside plot area
```

# Testing to see if players make choices significantly different from chance

Read the combined main task data from above
```{r}
rm(list=ls())

data <- read_csv(here("data", "preprocessed", "otree", "sessions", "main_task_combined_filtered.csv"), show_col_types = FALSE)
```

Check player choice accuracy across valid trials for both choices combined
Run binomial tests to check if the player choice accuracy is significantly different from chance, for choice 1 and choice 2 separately and combined
```{r}
# Calculate the player choice accuracy across valid trials
summary_df <- data %>%
  group_by(participant.id_in_session) %>%
  summarise(
    total_choice1_accuracy = sum(ifelse(player.computer_choice_one != 1, player.choice1_accuracy, 0), na.rm = TRUE),
    total_choice2_accuracy = sum(ifelse(player.computer_choice_two != 1, player.choice2_accuracy, 0), na.rm = TRUE),
    number_of_trials = n(),
    valid_trials_choice1 = sum(player.computer_choice_one != 1),
    valid_trials_choice2 = sum(player.computer_choice_two != 1)
  )

# Add binomial test results and percentage accuracy for all three categories
summary_df <- summary_df %>%
  mutate(
    # Choice 1
    percentage_accuracy_choice1 = (total_choice1_accuracy / valid_trials_choice1) * 100,
    binom_p_value_choice1 = map2_dbl(
      total_choice1_accuracy, valid_trials_choice1,
      ~binom.test(.x, .y, p = 0.5)$p.value
    ),
    # Choice 2
    percentage_accuracy_choice2 = (total_choice2_accuracy / valid_trials_choice2) * 100,
    binom_p_value_choice2 = map2_dbl(
      total_choice2_accuracy, valid_trials_choice2,
      ~binom.test(.x, .y, p = 0.5)$p.value
    ),
    # Combined (keeping your existing calculations)
    total_combined_accuracy = total_choice1_accuracy + total_choice2_accuracy,
    total_valid_trials = valid_trials_choice1 + valid_trials_choice2,
    percentage_accuracy_combined = (total_combined_accuracy / total_valid_trials) * 100,
    binom_p_value_combined = map2_dbl(
      total_combined_accuracy, total_valid_trials,
      ~binom.test(.x, .y, p = 0.5)$p.value
    )
  )

# Look at significant results for all three categories
significant_results <- summary_df %>%
  summarise(
    significant_choice1 = sum(binom_p_value_choice1 < 0.05, na.rm = TRUE),
    significant_choice2 = sum(binom_p_value_choice2 < 0.05, na.rm = TRUE),
    significant_combined = sum(binom_p_value_combined < 0.05, na.rm = TRUE),
    total_participants = n(),
    mean_accuracy_choice1 = mean(percentage_accuracy_choice1),
    sd_accuracy_choice1 = sd(percentage_accuracy_choice1),
    mean_accuracy_choice2 = mean(percentage_accuracy_choice2),
    sd_accuracy_choice2 = sd(percentage_accuracy_choice2),
    mean_accuracy_combined = mean(percentage_accuracy_combined),
    sd_accuracy_combined = sd(percentage_accuracy_combined)
  )

# Individual results
summary_df %>%
  select(participant.id_in_session, 
         percentage_accuracy_choice1, percentage_accuracy_choice2, percentage_accuracy_combined,
         binom_p_value_choice1, binom_p_value_choice2, binom_p_value_combined) %>%
  mutate(across(starts_with("percentage"), ~round(., 2)),
         across(starts_with("binom"), ~round(., 3)))

# Aggregate tests for all three categories
aggregate_test_choice1 <- binom.test(
  sum(summary_df$total_choice1_accuracy), 
  sum(summary_df$valid_trials_choice1), 
  p = 0.5
)

aggregate_test_choice2 <- binom.test(
  sum(summary_df$total_choice2_accuracy), 
  sum(summary_df$valid_trials_choice2), 
  p = 0.5
)

aggregate_test_combined <- binom.test(
  sum(summary_df$total_combined_accuracy), 
  sum(summary_df$total_valid_trials), 
  p = 0.5
)

# Print aggregate results
print("Aggregate results for Choice 1:")
print(aggregate_test_choice1)
print("Aggregate results for Choice 2:")
print(aggregate_test_choice2)
print("Aggregate results for Combined Choices:")
print(aggregate_test_combined)

# Create long format data for plotting
plot_data <- summary_df %>%
  select(participant.id_in_session, 
         Choice1 = percentage_accuracy_choice1,
         Choice2 = percentage_accuracy_choice2,
         Combined = percentage_accuracy_combined) %>%
  pivot_longer(cols = c(Choice1, Choice2, Combined),
               names_to = "choice_type",
               values_to = "accuracy")

# Calculate means for labels
means <- plot_data %>%
  group_by(choice_type) %>%
  summarise(mean_accuracy = mean(accuracy, na.rm = TRUE))

# Create the plot
ggplot(plot_data, aes(x = choice_type, y = accuracy)) +
  geom_violin(fill = "gray90", alpha = 0.5) +
  geom_hline(yintercept = 50, linetype = "dashed", color = "red", alpha = 0.7) +
  geom_jitter(width = 0.1, alpha = 0.6, size = 0.5) +
  geom_point(data = means, aes(y = mean_accuracy), 
             color = "red", size = 3) +
  geom_text(data = means, 
            aes(y = 110, label = sprintf("%.1f", mean_accuracy)),
            size = 4.5) +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    plot.margin = margin(1, 0.5, 0.5, 1, "cm")
  ) +
  labs(x = NULL,
       y = "Percentage Accuracy",
       title = NULL) +
  scale_y_continuous(limits = c(-5, 120))
```


# Subsetting the Qualtrics data and combining with oTree data
```{r}
rm(list=ls())

# Read and subset data (change the file path to the recent Qualtrics data)
data <- read_csv(here("data", "raw", "qualtrics", "sessions", "qualtrics_2025-06-03.csv"))[, c("Finished", "QID10", "QID31",
                paste0("SC", 1:19), "SC21", "SC22", "SC23", "SC24")]

# Set column names from first row and remove top 2 rows
colnames(data) <- as.character(data[1,])
data <- data[-c(1,2),]

# Rename id/age columns  
colnames(data)[2:3] <- c("id", "age")

# Set final column order using original column names
data <- data[, c("Finished", "id", "age", "EDUCATION", "GENDER",
           "LSAS-P", "LSAS-S", "DASS-A", "DASS-D", "DASS-S",
           "SSMS-CD", "SSMS-IA", "SRP-SF-IPM", "SRP-SF-CA", 
           "SRP-SF-ELS", "SRP-SF-CT", "AMI-ES", "AMI-SM", 
           "AMI-BA", "SSMS", "DASS", "LSAS", "SRP-SF", 
           "AMI", "AQ-10", "CHECKS")]

# Now rename education/gender to lowercase
colnames(data)[colnames(data) == "EDUCATION"] <- "education"
colnames(data)[colnames(data) == "GENDER"] <- "gender"

# Remove rows where Finished is not 1 and where checks is not 3
data <- data %>% filter(Finished == 1, CHECKS == 3)

# Save the preprocessed data
write_csv(data, here("data", "preprocessed", "qualtrics", "sessions", "qualtrics_2025-06-03_preprocessed.csv"))
```

Remove duplicate IDs from the Qualtrics data
```{r}
# Read the preprocessed Qualtrics data
data <- read_csv(here("data", "preprocessed", "qualtrics", "sessions", "qualtrics_2025-06-03_preprocessed.csv"))

# Check how many rows before deduplication
original_rows <- nrow(data)

# Keep only the first occurrence of each ID
data_deduplicated <- data %>%
  distinct(id, .keep_all = TRUE)

# Check how many rows were removed
rows_removed <- original_rows - nrow(data_deduplicated)
if(rows_removed > 0) {
  message(paste("Removed", rows_removed, "duplicate rows"))
} else {
  message("No duplicate IDs found")
}

# Save the deduplicated data back to the same file
write_csv(data_deduplicated, here("data", "preprocessed", "qualtrics", "sessions", "qualtrics_2025-06-03_preprocessed.csv"))
```

Psychological measures histogram from Qualtrics data
```{r}
# Read the preprocessed Qualtrics data
data <- read_csv(here("data", "preprocessed", "qualtrics", "sessions", "qualtrics_2025-06-03_preprocessed.csv"), show_col_types = FALSE)

# Prepare data for psychological measures
psych_data <- data %>%
  select(SSMS, DASS, LSAS, `SRP-SF`, AMI, `AQ-10`) %>%
  pivot_longer(cols = everything(), 
               names_to = "variable", 
               values_to = "value")

# Calculate means for psychological measures
psych_means <- data %>%
  select(SSMS, DASS, LSAS, `SRP-SF`, AMI, `AQ-10`) %>%
  summarise(across(everything(), ~mean(., na.rm = TRUE))) %>%
  pivot_longer(cols = everything(), 
               names_to = "variable", 
               values_to = "mean_val")

# Create color palette
colors <- c("skyblue", "lightgreen", "salmon", "purple", "orange", "pink")
line_colors <- c("darkblue", "darkgreen", "darkred", "darkmagenta", "darkorange", "deeppink")

# Split the data to handle AQ-10 and SSMS separately
aq10_data <- psych_data %>% filter(variable == "AQ-10")
ssms_data <- psych_data %>% filter(variable == "SSMS")
other_psych_data <- psych_data %>% filter(!variable %in% c("AQ-10", "SSMS"))

# Create the histogram facet grid for psychological measures
psych_plot <- ggplot() +
  # Regular histograms for all other variables
  geom_histogram(data = other_psych_data, 
                 aes(x = value, fill = variable), 
                 color = "white", alpha = 0.8) +
  # Specific histogram for AQ-10 with binwidth=1
  geom_histogram(data = aq10_data, 
                 aes(x = value, fill = variable), 
                 color = "white", alpha = 0.8,
                 binwidth = 1) +
  # Specific histogram for SSMS with binwidth=1
  geom_histogram(data = ssms_data, 
                 aes(x = value, fill = variable), 
                 color = "white", alpha = 0.8,
                 binwidth = 1) +
  # Add mean lines for all psychological measures
  geom_vline(data = psych_means,
             aes(xintercept = mean_val), 
             color = "red", linetype = "dashed", linewidth = 1) +
  facet_wrap(~ variable, scales = "free", ncol = 3) +
  theme_minimal() +
  labs(title = "Distribution of Psychological Measures",
       x = NULL,
       y = "Count") +
  scale_fill_manual(values = colors) +
  scale_color_manual(values = line_colors) +
  theme(
    strip.background = element_rect(fill = "lightgray", color = NA),
    strip.text = element_text(face = "bold"),
    panel.grid.minor = element_blank(),
    legend.position = "none"
  )

# Print the plot
print(psych_plot)
```

Demographics
```{r}
# Demographic plots - separate graphs

# Age histogram with mean line and value
age_mean <- mean(data$age, na.rm = TRUE)
age_plot <- ggplot(data, aes(x = age)) +
  geom_histogram(fill = "skyblue", color = "white", alpha = 0.8) +
  geom_vline(xintercept = age_mean, color = "red", linetype = "dashed", linewidth = 1) +
  annotate("text", x = age_mean, y = max(hist(data$age, plot = FALSE)$counts)/2, 
           label = sprintf("Mean: %.1f", age_mean), color = "red", hjust = -0.2) +
  theme_minimal() +
  labs(title = "Distribution of Age",
       x = "Age",
       y = "Count") +
  theme(panel.grid.minor = element_blank())

# Education histogram with counts on top of bars
education_count <- data %>%
  group_by(education) %>%
  summarise(count = n()) %>%
  filter(!is.na(education))

education_plot <- ggplot(data, aes(x = education)) +
  geom_histogram(fill = "lightgreen", color = "white", alpha = 0.8, stat = "count") +
  geom_text(data = education_count, 
            aes(x = education, y = count, label = count),
            vjust = -0.5, size = 3.5) +
  theme_minimal() +
  labs(title = "Distribution of Education Level",
       x = "Education Level",
       y = "Count") +
  theme(panel.grid.minor = element_blank())

# Gender bar chart with counts and percentages
# First create a count table with percentages
total_valid_gender <- sum(data$gender %in% c(1, 2), na.rm = TRUE)
gender_counts <- data %>%
  filter(gender %in% c(1, 2)) %>%
  count(gender) %>%
  mutate(
    gender_label = ifelse(gender == 1, "Male", "Female"),
    percentage = n / total_valid_gender * 100,
    label = sprintf("%d (%.1f%%)", n, percentage)
  )

# Then plot - thinner version
gender_plot <- ggplot(gender_counts, aes(x = gender_label, y = n, fill = gender_label)) +
  geom_bar(stat = "identity", color = "white", alpha = 0.8, width = 0.5) + # Made bars thinner
  geom_text(aes(label = label), vjust = -0.5, size = 3.5) +
  scale_fill_manual(values = c("Male" = "steelblue", "Female" = "salmon")) +
  theme_minimal() +
  labs(title = "Gender Distribution",
       x = NULL,
       y = "Count") +
  theme(
    panel.grid.minor = element_blank(),
    legend.position = "none",
    plot.margin = margin(r = 100, l = 100, unit = "pt") # Added margins to make plot thinner
  )

# Display the plots
print(age_plot)
print(education_plot)
print(gender_plot)
```

Questionnaires split by gender and age
```{r, fig.width=10, fig.height=6}

# 1. IMPROVED BAR CHART FACET GRID
# ----------------------------------------------------

# Reshape data for t-tests
questionnaire_data_long <- data %>%
  filter(gender %in% c(1, 2)) %>%
  mutate(gender_label = ifelse(gender == 1, "Male", "Female")) %>%
  select(gender_label, SSMS, DASS, LSAS, `SRP-SF`, AMI, `AQ-10`) %>%
  pivot_longer(
    cols = -gender_label,
    names_to = "measure",
    values_to = "score"
  )

# Run t-tests for each questionnaire
t_test_results <- questionnaire_data_long %>%
  group_by(measure) %>%
  t_test(score ~ gender_label) %>%
  add_significance() %>%
  mutate(
    p.signif = case_when(
      p < 0.001 ~ "***",
      p < 0.01 ~ "**", 
      p < 0.05 ~ "*",
      TRUE ~ "ns"
    ),
    p.label = case_when(
      p < 0.001 ~ "p < 0.001",
      TRUE ~ sprintf("p = %.3f", p)
    )
  )

# Calculate means and standard errors
questionnaire_means <- data %>%
  filter(gender %in% c(1, 2)) %>%
  mutate(gender_label = ifelse(gender == 1, "Male", "Female")) %>%
  group_by(gender_label) %>%
  summarise(across(c(SSMS, DASS, LSAS, `SRP-SF`, AMI, `AQ-10`), 
                  list(mean = ~mean(., na.rm = TRUE), 
                       se = ~sd(., na.rm = TRUE) / sqrt(sum(!is.na(.)))))) %>%
  pivot_longer(
    cols = -gender_label,
    names_to = c("measure", ".value"),
    names_pattern = "(.+)_(mean|se)"
  )

# Calculate appropriate y-axis limits for each measure
y_limits <- questionnaire_means %>%
  group_by(measure) %>%
  summarise(
    max_val = max(mean + se, na.rm = TRUE),
    min_val = min(mean - se, na.rm = TRUE)
  ) %>%
  mutate(
    y_max = max_val * 1.3,  # Add 30% space above the highest bar+error
    y_min = min(0, min_val * 1.1)  # Include zero or go 10% below lowest value if negative
  )

# Join t-test results with y-limits data
t_test_results <- t_test_results %>%
  left_join(y_limits, by = "measure") %>%
  mutate(
    # Position the significance bracket at 85% of the plot height
    y.position = y_min + 0.85 * (y_max - y_min),
    # Position the p-value text lower
    p.position = y.position - 0.05 * (y_max - y_min)
  )

# Create the improved bar plot
gender_comparison_plot <- ggplot(questionnaire_means, 
                              aes(x = gender_label, y = mean, fill = gender_label)) +
  geom_bar(stat = "identity", position = position_dodge(), width = 0.7, color = "black") +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), 
                position = position_dodge(0.7), width = 0.25) +
  # Add significance brackets
  geom_bracket(
    data = t_test_results,
    aes(xmin = 1, xmax = 2, y.position = y.position, label = p.signif),
    inherit.aes = FALSE,
    tip.length = 0.02,
    bracket.size = 0.5
  ) +
  # Add p-value text below the bracket
  geom_text(
    data = t_test_results,
    aes(x = 1.5, y = p.position, label = p.label),
    inherit.aes = FALSE,
    size = 2.8
  ) +
  # Set y-axis limits based on calculated values
  facet_wrap(~ measure, scales = "free_y", ncol = 3) +
  scale_fill_manual(values = c("Male" = "#4472C4", "Female" = "#ED7D31")) +
  labs(
    title = "Mean Scores by Gender Across Psychological Measures",
    x = NULL,
    y = "Mean Score ( SE)",
    fill = NULL
  ) +
  theme_pubr() +
  theme(
    strip.background = element_rect(fill = "white", color = "black"),
    strip.text = element_text(face = "bold", size = 11),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    legend.position = "bottom",
    panel.grid.major.y = element_line(color = "gray90"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    plot.title = element_text(size = 14, hjust = 0.5)
  )

# Manually set y-axis limits for each facet
gender_comparison_plot <- gender_comparison_plot +
  facetted_pos_scales(
    y = lapply(
      split(y_limits, y_limits$measure),
      function(df) {
        scale_y_continuous(limits = c(df$y_min, df$y_max))
      }
    )
  )

# 2. IMPROVED SCATTER PLOT FACET GRID
# ----------------------------------------------------

# Prepare data for correlation plots
age_correlations_data <- data %>%
  select(age, SSMS, DASS, LSAS, `SRP-SF`, AMI, `AQ-10`) %>%
  pivot_longer(
    cols = -age,
    names_to = "measure",
    values_to = "score"
  )

# Calculate correlation coefficients and p-values
cor_results <- age_correlations_data %>%
  group_by(measure) %>%
  summarise(
    r = cor(age, score, use = "pairwise.complete.obs"),
    p_value = cor.test(age, score, use = "pairwise.complete.obs")$p.value
  ) %>%
  mutate(
    significance = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01 ~ "**",
      p_value < 0.05 ~ "*",
      TRUE ~ "ns"
    ),
    p_label = case_when(
      p_value < 0.001 ~ "p < 0.001",
      TRUE ~ sprintf("p = %.3f", p_value)
    ),
    # Create combined label with r and p on separate lines
    label = sprintf("r = %.2f%s\n%s", r, significance, p_label)
  )

# Create the improved correlation plots
age_correlation_plot <- ggplot(age_correlations_data, aes(x = age, y = score)) +
  geom_point(alpha = 0.6, size = 1.5, color = "#4472C4") +
  geom_smooth(method = "lm", color = "#D55E00", fill = "#D55E0080") +
  geom_text(
    data = cor_results,
    aes(label = label),
    x = Inf, y = Inf,
    hjust = 1.1, vjust = 1.2,
    size = 3,
    lineheight = 0.8
  ) +
  facet_wrap(~ measure, scales = "free_y", ncol = 3) +
  labs(
    title = "Relationship Between Age and Psychological Measures",
    x = "Age (years)",
    y = "Score"
  ) +
  theme_pubr() +
  theme(
    strip.background = element_rect(fill = "white", color = "black"),
    strip.text = element_text(face = "bold", size = 11),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    panel.grid.major = element_line(color = "gray90"),
    panel.grid.minor = element_blank(),
    plot.title = element_text(size = 14, hjust = 0.5)
  )

# Display the plots
print(gender_comparison_plot)
print(age_correlation_plot)
```


Add Qualtrics questionnaire data to oTree data based on shared Prolific ID and organise properly
```{r}
rm(list=ls())

otree_data <- read.csv(here("data", "preprocessed", "otree", "sessions", "main_task_combined_filtered.csv"))
qualtrics_data <- read.csv(here("data", "preprocessed", "qualtrics", "sessions", "qualtrics_2025-06-03_preprocessed.csv"))

# First, create a copy of qualtrics_data without the CHECKS and finished columns
qualtrics_clean <- qualtrics_data[, !colnames(qualtrics_data) %in% c("CHECKS", "Finished")]

# Convert column names to lowercase and replace dots with underscores
colnames(qualtrics_clean) <- tolower(gsub("\\.", "_", colnames(qualtrics_clean)))

# Merge the datasets based on the ID columns
merged_data <- merge(otree_data, 
                    qualtrics_clean,
                    by.x = "participant.label",
                    by.y = "id",
                    all.x = TRUE)

# Sort by trial number and participant id number
merged_data <- merged_data[order(merged_data$subsession.round_number, 
                                      merged_data$participant.id_in_session), ]

# Save the preprocessed data (remove pilots if not a pilot)
write_csv(merged_data, here("data", "preprocessed", "merged", "sessions", "otree_prolific_merged_filtered_2025-06-03.csv"))
```

# Check split of reaction times per trial per decision
```{r}
rm(list=ls())
# Read the combined data
data <- read_csv(here("data", "preprocessed", "merged", "sessions", "otree_prolific_merged_filtered_2025-06-03.csv"), show_col_types = FALSE)

# Create output directory if it doesn't exist
dir.create(here("output", "preprocessing"), recursive = TRUE, showWarnings = FALSE)

# First set of histograms
par(mfrow=c(2,2))
hist(data$player.initial_choice_time[data$player.initial_choice_time <= 3], 
     main="Initial Choice Time", xlab="Time", col="skyblue", border="white")
hist(data$player.initial_bet_time[data$player.initial_bet_time <= 3], 
     main="Initial Bet Time", xlab="Time", col="lightgreen", border="white")
hist(data$player.second_choice_time[data$player.second_choice_time <= 3], 
     main="Second Choice Time", xlab="Time", col="salmon", border="white")
hist(data$player.second_bet_time[data$player.second_bet_time <= 3], 
     main="Second Bet Time", xlab="Time", col="purple", border="white")

# Save histograms
ggsave(here("output", "preprocessing", "time_histograms.pdf"), width = 10, height = 8)

# Calculate aggregated data
meanIC <- aggregate(player.initial_choice_time ~ group.trial_number, data=data, FUN=mean)
meanIB <- aggregate(player.initial_bet_time ~ group.trial_number, data=data, FUN=mean)
meanSC <- aggregate(player.second_choice_time ~ group.trial_number, data=data, FUN=mean)
meanSB <- aggregate(player.second_bet_time ~ group.trial_number, data=data, FUN=mean)
sumCC1 <- aggregate(player.computer_choice_one ~ group.trial_number, data=data, FUN=sum)
sumCC2 <- aggregate(player.computer_choice_two ~ group.trial_number, data=data, FUN=sum)
sumCB1 <- aggregate(player.computer_bet_one ~ group.trial_number, data=data, FUN=sum)
sumCB2 <- aggregate(player.computer_bet_two ~ group.trial_number, data=data, FUN=sum)

# Second set of plots (means by trial number)
par(mfrow=c(2,2))
plot(meanIC, type="l", main="Mean Initial Choice Time", 
     xlab="Trial Number", ylab="Mean Time", col="blue", lwd=2)
plot(meanIB, type="l", main="Mean Initial Bet Time", 
     xlab="Trial Number", ylab="Mean Time", col="green", lwd=2)
plot(meanSC, type="l", main="Mean Second Choice Time", 
     xlab="Trial Number", ylab="Mean Time", col="red", lwd=2)
plot(meanSB, type="l", main="Mean Second Bet Time", 
     xlab="Trial Number", ylab="Mean Time", col="orange", lwd=2)

# Save mean plots
ggsave(here("output", "preprocessing", "mean_time_by_trial.pdf"), width = 10, height = 8)

# Third set of plots (sums by trial number)
par(mfrow=c(2,2))
plot(sumCC1, type="l", main="Sum of Computer Choice One", 
     xlab="Trial Number", ylab="Sum", col="purple", lwd=2)
plot(sumCC2, type="l", main="Sum of Computer Choice Two", 
     xlab="Trial Number", ylab="Sum", col="brown", lwd=2)
plot(sumCB1, type="l", main="Sum of Computer Bet One", 
     xlab="Trial Number", ylab="Sum", col="darkgreen", lwd=2)
plot(sumCB2, type="l", main="Sum of Computer Bet Two", 
     xlab="Trial Number", ylab="Sum", col="darkblue", lwd=2)

# Save sum plots
ggsave(here("output", "preprocessing", "sum_computer_by_trial.pdf"), width = 10, height = 8)

# Reset the plotting layout
par(mfrow=c(1,1))
```

# Add combined submission data to main task data
```{r}
rm(list=ls())

# Read the combined main task data
main_data <- read_csv(here("data", "preprocessed", "merged", "sessions", "otree_prolific_merged_filtered_2025-06-03.csv"), show_col_types = FALSE)

# Read the combined submission data
submission_data <- read_csv(here("data", "preprocessed", "otree", "sessions", "combined_filtered_submissions.csv"), show_col_types = FALSE)

# Select only the columns we want to add from submission_data
submission_subset <- submission_data %>%
  select(participant.label,
         player.main_task_bonus,
         player.task_understanding,
         player.task_difficulty,
         player.engagement,
         player.influence,
         player.real_players,
         player.attention_focus,
         player.main_task_group_id)

# Join the datasets based on participant.label
merged_data <- main_data %>%
  left_join(submission_subset, by = "participant.label")

# Save the merged data back to the original file
write_csv(merged_data, 
          here("data", "preprocessed", "merged", "sessions", "otree_prolific_merged_filtered_2025-06-03.csv"))
```

# Justify data cleaning by plotting how many trials have manual choices/bets and how many are made by the computer
```{r, fig.width=6, fig.height=6}
rm(list=ls())

# Function to create and plot the counts summary for any dataset
create_manual_vs_computer_plot <- function(data, title) {
  # Select the columns of interest and reshape to long format
  counts_data <- data %>%
    select(
      player.computer_choice_one,
      player.computer_bet_one,
      player.computer_choice_two,
      player.computer_bet_two
    ) %>%
    rename(
      "Choice 1" = player.computer_choice_one,
      "Bet 1" = player.computer_bet_one,
      "Choice 2" = player.computer_choice_two,
      "Bet 2" = player.computer_bet_two
    ) %>%
    pivot_longer(
      cols = everything(),
      names_to = "variable",
      values_to = "code"
    ) %>%
    filter(!is.na(code)) %>%
    mutate(
      type = ifelse(code == 0, "Manual", "Computer"),
      variable = factor(variable, levels = c("Choice 1", "Bet 1", "Choice 2", "Bet 2"))
    )
  
  # Count occurrences
  counts_summary <- counts_data %>%
    count(variable, type) %>%
    group_by(variable) %>%
    mutate(percentage = n / sum(n) * 100) %>%
    ungroup() %>%
    # Make sure "Manual" comes before "Computer" in the plot
    mutate(type = factor(type, levels = c("Manual", "Computer")))
  
  # Create the faceted plot
  ggplot(counts_summary, aes(x = type, y = n, fill = type)) +
    geom_col(width = 0.7) +
    # Manual bars - text inside
    geom_text(data = subset(counts_summary, type == "Manual"),
              aes(label = sprintf("%d\n(%.1f%%)", n, percentage)), 
              position = position_stack(vjust = 0.5),
              size = 4) +
    # Computer bars - text above
    geom_text(data = subset(counts_summary, type == "Computer"),
              aes(label = sprintf("%d\n(%.1f%%)", n, percentage)), 
              vjust = -0.5,  # Places text above the bar
              size = 4) +
    facet_wrap(~ variable, nrow = 2, ncol = 2) +
    scale_fill_manual(values = c("Manual" = "skyblue", "Computer" = "salmon")) +
    labs(
      title = title,
      x = NULL,
      y = "Count",
      fill = "Type"
    ) +
    theme_minimal() +
    theme(
      axis.title = element_text(size = 14),
      axis.text = element_text(size = 12),
      strip.text = element_text(size = 14, face = "bold"),
      panel.spacing = unit(1, "lines"),
      # Add some more space at the top for the labels
      plot.margin = margin(t = 20, r = 10, b = 10, l = 10, unit = "pt")
    )
}

# Read the first dataset (filtered data)
data_filtered <- read_csv(here("data", "preprocessed", "merged", "sessions", "otree_prolific_merged_filtered_2025-06-03.csv"), 
                        show_col_types = FALSE)

# Read the second dataset (unfiltered data)
data_unfiltered <- read_csv(here("data", "preprocessed", "otree", "sessions", "combined_main_task.csv"), 
                           show_col_types = FALSE)

# Create plot for filtered data
plot_filtered <- create_manual_vs_computer_plot(data_filtered, "Manual vs. Computer Choices and Bets (Filtered Data)")

# Create plot for unfiltered data
plot_unfiltered <- create_manual_vs_computer_plot(data_unfiltered, "Manual vs. Computer Choices and Bets (Unfiltered Data)")

# Display plots
print(plot_filtered)
print(plot_unfiltered)
```

Number of decisions that took 3 seconds versus number which didn't
```{r, fig.width=6, fig.height=10}
rm(list=ls())

# Function to create the first plot: time == 3 vs time != 3
create_time_comparison_plot <- function(data, title) {
  # Select the columns of interest and reshape to long format
  time_data <- data %>%
    select(
      player.initial_choice_time,
      player.initial_bet_time,
      player.second_choice_time,
      player.second_bet_time
    ) %>%
    rename(
      "Initial Choice" = player.initial_choice_time,
      "Initial Bet" = player.initial_bet_time,
      "Second Choice" = player.second_choice_time,
      "Second Bet" = player.second_bet_time
    ) %>%
    pivot_longer(
      cols = everything(),
      names_to = "variable",
      values_to = "time"
    ) %>%
    filter(!is.na(time)) %>%
    mutate(
      time_category = ifelse(time == 3, "Time = 3", "Time  3"),
      variable = factor(variable, levels = c("Initial Choice", "Initial Bet", "Second Choice", "Second Bet"))
    )
  
  # Count occurrences
  time_summary <- time_data %>%
    count(variable, time_category) %>%
    group_by(variable) %>%
    mutate(percentage = n / sum(n) * 100) %>%
    ungroup() %>%
    # Make sure "Time = 3" comes before "Time  3" in the plot
    mutate(time_category = factor(time_category, levels = c("Time = 3", "Time  3")))
  
  # Create the faceted plot
  ggplot(time_summary, aes(x = time_category, y = n, fill = time_category)) +
    geom_col(width = 0.7) +
    geom_text(aes(label = sprintf("%d\n(%.1f%%)", n, percentage)), 
              position = position_stack(vjust = 0.5),
              size = 4) +
    facet_wrap(~ variable, nrow = 2, ncol = 2) +
    scale_fill_manual(values = c("Time = 3" = "skyblue", "Time  3" = "orange")) +
    labs(
      title = title,
      x = NULL,
      y = "Count",
      fill = "Time Category"
    ) +
    theme_minimal() +
    theme(
      axis.title = element_text(size = 14),
      axis.text = element_text(size = 12),
      strip.text = element_text(size = 14, face = "bold"),
      panel.spacing = unit(1, "lines"),
      plot.margin = margin(t = 20, r = 10, b = 10, l = 10, unit = "pt")
    )
}

# Function to create the second plot: manual vs computer for time == 3
create_time3_manual_vs_computer_plot <- function(data, title) {
  # Create a dataframe for initial choice where time == 3
  initial_choice_data <- data %>%
    filter(player.initial_choice_time == 3, !is.na(player.computer_choice_one)) %>%
    mutate(
      variable = "Initial Choice",
      type = ifelse(player.computer_choice_one == 0, "Manual", "Computer")
    ) %>%
    select(variable, type)
  
  # Create a dataframe for initial bet where time == 3
  initial_bet_data <- data %>%
    filter(player.initial_bet_time == 3, !is.na(player.computer_bet_one)) %>%
    mutate(
      variable = "Initial Bet",
      type = ifelse(player.computer_bet_one == 0, "Manual", "Computer")
    ) %>%
    select(variable, type)
  
  # Create a dataframe for second choice where time == 3
  second_choice_data <- data %>%
    filter(player.second_choice_time == 3, !is.na(player.computer_choice_two)) %>%
    mutate(
      variable = "Second Choice",
      type = ifelse(player.computer_choice_two == 0, "Manual", "Computer")
    ) %>%
    select(variable, type)
  
  # Create a dataframe for second bet where time == 3
  second_bet_data <- data %>%
    filter(player.second_bet_time == 3, !is.na(player.computer_bet_two)) %>%
    mutate(
      variable = "Second Bet",
      type = ifelse(player.computer_bet_two == 0, "Manual", "Computer")
    ) %>%
    select(variable, type)
  
  # Combine all dataframes
  combined_data <- bind_rows(
    initial_choice_data,
    initial_bet_data,
    second_choice_data,
    second_bet_data
  ) %>%
    mutate(variable = factor(variable, levels = c("Initial Choice", "Initial Bet", "Second Choice", "Second Bet")))
  
  # Count occurrences
  counts_summary <- combined_data %>%
    count(variable, type) %>%
    group_by(variable) %>%
    mutate(percentage = n / sum(n) * 100) %>%
    ungroup() %>%
    # Make sure "Manual" comes before "Computer" in the plot
    mutate(type = factor(type, levels = c("Manual", "Computer")))
  
  # Create the faceted plot
  ggplot(counts_summary, aes(x = type, y = n, fill = type)) +
    geom_col(width = 0.7) +
    geom_text(aes(label = sprintf("%d\n(%.1f%%)", n, percentage)), 
              position = position_stack(vjust = 0.5),
              size = 4) +
    facet_wrap(~ variable, nrow = 2, ncol = 2) +
    scale_fill_manual(values = c("Manual" = "skyblue", "Computer" = "salmon")) +
    labs(
      title = title,
      x = NULL,
      y = "Count",
      fill = "Type"
    ) +
    theme_minimal() +
    theme(
      axis.title = element_text(size = 14),
      axis.text = element_text(size = 12),
      strip.text = element_text(size = 14, face = "bold"),
      panel.spacing = unit(1, "lines"),
      plot.margin = margin(t = 20, r = 10, b = 10, l = 10, unit = "pt")
    )
}

# Read the datasets
data_filtered <- read_csv(here("data", "preprocessed", "merged", "sessions", "otree_prolific_merged_filtered_2025-06-03.csv"), 
                         show_col_types = FALSE)
data_unfiltered <- read_csv(here("data", "preprocessed", "otree", "sessions", "combined_main_task.csv"), 
                           show_col_types = FALSE)

# Create and display the first plots (time == 3 vs time != 3)
plot_time_filtered <- create_time_comparison_plot(data_filtered, "Time = 3 vs Time  3 (Filtered Data)")
plot_time_unfiltered <- create_time_comparison_plot(data_unfiltered, "Time = 3 vs Time  3 (Unfiltered Data)")

# Display the first plots
print(plot_time_filtered)
print(plot_time_unfiltered)

# Create and display the second plots (manual vs computer for time == 3)
plot_time3_filtered <- create_time3_manual_vs_computer_plot(data_filtered, "Manual vs. Computer for Time = 3 (Filtered Data)")
plot_time3_unfiltered <- create_time3_manual_vs_computer_plot(data_unfiltered, "Manual vs. Computer for Time = 3 (Unfiltered Data)")

# Display the second plots
print(plot_time3_filtered)
print(plot_time3_unfiltered)
```

```{r, fig.width=6, fig.height=10}
# Function to create a plot comparing time == 0 vs time != 0
create_time_zero_comparison_plot <- function(data, title) {
  # Select the columns of interest and reshape to long format
  time_data <- data %>%
    select(
      player.initial_choice_time,
      player.initial_bet_time,
      player.second_choice_time,
      player.second_bet_time
    ) %>%
    rename(
      "Initial Choice" = player.initial_choice_time,
      "Initial Bet" = player.initial_bet_time,
      "Second Choice" = player.second_choice_time,
      "Second Bet" = player.second_bet_time
    ) %>%
    pivot_longer(
      cols = everything(),
      names_to = "variable",
      values_to = "time"
    ) %>%
    filter(!is.na(time)) %>%
    mutate(
      time_category = ifelse(time == 0, "Time = 0", "Time  0"),
      variable = factor(variable, levels = c("Initial Choice", "Initial Bet", "Second Choice", "Second Bet"))
    )
  
  # Count occurrences
  time_summary <- time_data %>%
    count(variable, time_category) %>%
    group_by(variable) %>%
    mutate(percentage = n / sum(n) * 100) %>%
    ungroup() %>%
    # Make sure "Time = 0" comes before "Time  0" in the plot
    mutate(time_category = factor(time_category, levels = c("Time = 0", "Time  0")))
  
  # Create the faceted plot
  ggplot(time_summary, aes(x = time_category, y = n, fill = time_category)) +
    geom_col(width = 0.7) +
    geom_text(aes(label = sprintf("%d\n(%.1f%%)", n, percentage)), 
              position = position_stack(vjust = 0.5),
              size = 4) +
    facet_wrap(~ variable, nrow = 2, ncol = 2) +
    scale_fill_manual(values = c("Time = 0" = "lightgreen", "Time  0" = "coral")) +
    labs(
      title = title,
      x = NULL,
      y = "Count",
      fill = "Time Category"
    ) +
    theme_minimal() +
    theme(
      axis.title = element_text(size = 14),
      axis.text = element_text(size = 12),
      strip.text = element_text(size = 14, face = "bold"),
      panel.spacing = unit(1, "lines"),
      plot.margin = margin(t = 20, r = 10, b = 10, l = 10, unit = "pt")
    )
}

# Function to create a plot comparing time > 3 vs time <= 3
create_time_gt3_comparison_plot <- function(data, title) {
  # Select the columns of interest and reshape to long format
  time_data <- data %>%
    select(
      player.initial_choice_time,
      player.initial_bet_time,
      player.second_choice_time,
      player.second_bet_time
    ) %>%
    rename(
      "Initial Choice" = player.initial_choice_time,
      "Initial Bet" = player.initial_bet_time,
      "Second Choice" = player.second_choice_time,
      "Second Bet" = player.second_bet_time
    ) %>%
    pivot_longer(
      cols = everything(),
      names_to = "variable",
      values_to = "time"
    ) %>%
    filter(!is.na(time)) %>%
    mutate(
      time_category = ifelse(time > 3, "Time > 3", "Time  3"),
      variable = factor(variable, levels = c("Initial Choice", "Initial Bet", "Second Choice", "Second Bet"))
    )
  
  # Count occurrences
  time_summary <- time_data %>%
    count(variable, time_category) %>%
    group_by(variable) %>%
    mutate(percentage = n / sum(n) * 100) %>%
    ungroup() %>%
    # Make sure "Time > 3" comes before "Time  3" in the plot
    mutate(time_category = factor(time_category, levels = c("Time > 3", "Time  3")))
  
  # Create the faceted plot
  ggplot(time_summary, aes(x = time_category, y = n, fill = time_category)) +
    geom_col(width = 0.7) +
    geom_text(aes(label = sprintf("%d\n(%.1f%%)", n, percentage)), 
              position = position_stack(vjust = 0.5),
              size = 4) +
    facet_wrap(~ variable, nrow = 2, ncol = 2) +
    scale_fill_manual(values = c("Time > 3" = "purple", "Time  3" = "lightblue")) +
    labs(
      title = title,
      x = NULL,
      y = "Count",
      fill = "Time Category"
    ) +
    theme_minimal() +
    theme(
      axis.title = element_text(size = 14),
      axis.text = element_text(size = 12),
      strip.text = element_text(size = 14, face = "bold"),
      panel.spacing = unit(1, "lines"),
      plot.margin = margin(t = 20, r = 10, b = 10, l = 10, unit = "pt")
    )
}

# Create and display the plots for the filtered dataset only
plot_time_zero_filtered <- create_time_zero_comparison_plot(data_filtered, "Time = 0 vs Time  0 (Filtered Data)")
plot_time_gt3_filtered <- create_time_gt3_comparison_plot(data_filtered, "Time > 3 vs Time  3 (Filtered Data)")

# Display the plots
print(plot_time_zero_filtered)
print(plot_time_gt3_filtered)
```

# Split data by real players ratings
```{r, fig.width=10, fig.height=6}
rm(list=ls())

# Read the combined dataset
combined_data <- read_csv(here("data", "preprocessed", "merged", "sessions", "otree_prolific_merged_filtered_2025-06-03.csv"), 
                         show_col_types = FALSE)


# First, ensure we have only unique participants
unique_data <- combined_data %>%
  distinct(participant.label, .keep_all = TRUE)

# Calculate mean and median
mean_val <- mean(unique_data$player.real_players, na.rm = TRUE)
median_val <- median(unique_data$player.real_players, na.rm = TRUE)

# Create the histogram with bin width of 2
ggplot(unique_data, aes(x = player.real_players)) +
  geom_histogram(binwidth = 2, fill = "lightblue", color = "black") +
  # Add vertical line for mean
  geom_vline(aes(xintercept = mean_val), color = "red", linetype = "dashed", size = 1) +
  # Add vertical line for median
  geom_vline(aes(xintercept = median_val), color = "blue", linetype = "dashed", size = 1) +
  # Add labels for mean and median
  annotate("text", x = mean_val, y = Inf, label = paste("Mean =", round(mean_val, 2)), 
           vjust = 1.5, hjust = -0.1, color = "red") +
  annotate("text", x = median_val, y = Inf, label = paste("Median =", round(median_val, 2)), 
           vjust = 3, hjust = -0.1, color = "blue") +
  labs(x = "Real Players Belief (Rating 0-100", y = "Count") +
  scale_x_continuous(breaks = seq(min(unique_data$player.real_players, na.rm = TRUE), 
                                 max(unique_data$player.real_players, na.rm = TRUE), 
                                 by = 2)) +
  theme_minimal() +
  theme(panel.grid = element_blank(),
        panel.background = element_rect(fill = "white"),
        plot.background = element_rect(fill = "white"))

# First, extract the values and sort them
sorted_values <- unique_data %>%
  pull(player.real_players) %>%
  sort()

# Create a function to get the nth value
x <- function(n) {
  if(n <= 0 || n > length(sorted_values)) {
    return(paste("Error: Position", n, "is out of bounds. Valid range is 1 to", length(sorted_values)))
  }
  return(sorted_values[n])
}
```
Now let's get our thresholds for high and low belief

```{r}
# Define the thresholds
low_threshold <- 30
high_threshold <- 99

# First, examine the distribution of player.real_players scores
player_belief_summary <- combined_data %>%
  group_by(participant.label) %>%
  summarize(belief_score = first(player.real_players)) %>%
  arrange(belief_score)

# Get lists of participant IDs for high and low belief based on thresholds
high_belief_ids <- player_belief_summary %>%
  filter(belief_score > high_threshold) %>%
  pull(participant.label)

low_belief_ids <- player_belief_summary %>%
  filter(belief_score < low_threshold) %>%
  pull(participant.label)

# Create high belief and low belief datasets
high_belief_data <- combined_data %>%
  filter(participant.label %in% high_belief_ids)

low_belief_data <- combined_data %>%
  filter(participant.label %in% low_belief_ids)

# Create the output filenames
input_filename <- "otree_prolific_merged_filtered_2025-06-03.csv"
high_belief_filename <- gsub("\\.csv$", "_high_belief.csv", input_filename)
low_belief_filename <- gsub("\\.csv$", "_low_belief.csv", input_filename)

# Save the datasets
write_csv(high_belief_data, 
          here("data", "preprocessed", "merged", "sessions", high_belief_filename))

write_csv(low_belief_data, 
          here("data", "preprocessed", "merged", "sessions", low_belief_filename))

```


# Create dataList for stan modeling from combined dataset

```{r}
rm(list=ls())

# Read data
data <- read_csv(here("data", "preprocessed", "merged", "pilots", "otree_prolific_merged_filtered_2025-02-07.csv"), 
                 show_col_types = FALSE)

# Create new list
testdataList <- list()

# Get unique IDs and sort them
unique_ids <- sort(unique(data$participant.id_in_session))

# Set nSubjects and nTrials
testdataList$nSubjects <- as.numeric(length(unique_ids))
testdataList$nTrials <- as.integer(max(data$group.trial_number))

# Create 2D arrays
testdataList$choice1 <- array(NA, dim = c(testdataList$nSubjects, testdataList$nTrials))
testdataList$choice2 <- array(NA, dim = c(testdataList$nSubjects, testdataList$nTrials))
testdataList$bet1 <- array(NA, dim = c(testdataList$nSubjects, testdataList$nTrials))
testdataList$bet2 <- array(NA, dim = c(testdataList$nSubjects, testdataList$nTrials))
testdataList$choice1Acc <- array(NA, dim = c(testdataList$nSubjects, testdataList$nTrials))
testdataList$choice2Acc <- array(NA, dim = c(testdataList$nSubjects, testdataList$nTrials))
testdataList$reward <- array(NA, dim = c(testdataList$nSubjects, testdataList$nTrials))
testdataList$winprob <- array(NA, dim = c(testdataList$nSubjects, testdataList$nTrials))
testdataList$choice1with <- array(NA, dim = c(testdataList$nSubjects, testdataList$nTrials))
testdataList$choice1against <- array(NA, dim = c(testdataList$nSubjects, testdataList$nTrials))
testdataList$choice2with <- array(NA, dim = c(testdataList$nSubjects, testdataList$nTrials))
testdataList$choice2against <- array(NA, dim = c(testdataList$nSubjects, testdataList$nTrials))
testdataList$chswitch <- array(NA, dim = c(testdataList$nSubjects, testdataList$nTrials))

# Create 3D arrays
testdataList$otherChoice1 <- array(NA, dim = c(testdataList$nSubjects, testdataList$nTrials, 4))
testdataList$otherChoice2 <- array(NA, dim = c(testdataList$nSubjects, testdataList$nTrials, 4))
testdataList$otherChoice1Acc <- array(NA, dim = c(testdataList$nSubjects, testdataList$nTrials, 4))
testdataList$otherChoice2Acc <- array(NA, dim = c(testdataList$nSubjects, testdataList$nTrials, 4))
testdataList$otherReward <- array(NA, dim = c(testdataList$nSubjects, testdataList$nTrials, 4))

# Fill the arrays
for(subject_idx in 1:length(unique_ids)) {
    actual_id <- unique_ids[subject_idx]
    for(trial in 1:testdataList$nTrials) {
        subj_trial_idx <- which(data$participant.id_in_session == actual_id & 
                               data$group.trial_number == trial)
        
        if(length(subj_trial_idx) > 0) {
            # 3D arrays
            testdataList$otherChoice1[subject_idx, trial, ] <- c(
                data$player.player1_choice_one[subj_trial_idx],
                data$player.player2_choice_one[subj_trial_idx],
                data$player.player3_choice_one[subj_trial_idx],
                data$player.player4_choice_one[subj_trial_idx]
            )
            
            testdataList$otherChoice2[subject_idx, trial, ] <- c(
                data$player.player1_choice_two[subj_trial_idx],
                data$player.player2_choice_two[subj_trial_idx],
                data$player.player3_choice_two[subj_trial_idx],
                data$player.player4_choice_two[subj_trial_idx]
            )
            
            testdataList$otherChoice1Acc[subject_idx, trial, ] <- c(
                data$player.player1_choice1_accuracy[subj_trial_idx],
                data$player.player2_choice1_accuracy[subj_trial_idx],
                data$player.player3_choice1_accuracy[subj_trial_idx],
                data$player.player4_choice1_accuracy[subj_trial_idx]
            )
            
            testdataList$otherChoice2Acc[subject_idx, trial, ] <- c(
                data$player.player1_choice2_accuracy[subj_trial_idx],
                data$player.player2_choice2_accuracy[subj_trial_idx],
                data$player.player3_choice2_accuracy[subj_trial_idx],
                data$player.player4_choice2_accuracy[subj_trial_idx]
            )
            
            testdataList$otherReward[subject_idx, trial, ] <- c(
                data$player.player1_loss_or_gain[subj_trial_idx],
                data$player.player2_loss_or_gain[subj_trial_idx],
                data$player.player3_loss_or_gain[subj_trial_idx],
                data$player.player4_loss_or_gain[subj_trial_idx]
            )
            
            # 2D arrays
            testdataList$choice1[subject_idx, trial] <- data$player.chosen_image_one_binary[subj_trial_idx]
            testdataList$choice2[subject_idx, trial] <- data$player.chosen_image_two_binary[subj_trial_idx]
            testdataList$chswitch[subject_idx, trial] <- data$player.switch_vs_stay[subj_trial_idx]
            testdataList$bet1[subject_idx, trial] <- data$player.bet1[subj_trial_idx]
            testdataList$bet2[subject_idx, trial] <- data$player.bet2[subj_trial_idx]
            testdataList$reward[subject_idx, trial] <- data$player.trial_reward[subj_trial_idx]
            testdataList$winprob[subject_idx, trial] <- data$group.reward_probability_A[subj_trial_idx]
            testdataList$choice1Acc[subject_idx, trial] <- data$player.choice1_accuracy[subj_trial_idx]
            testdataList$choice2Acc[subject_idx, trial] <- data$player.choice2_accuracy[subj_trial_idx]
            testdataList$choice1with[subject_idx, trial] <- data$player.choice1_with[subj_trial_idx]
            testdataList$choice1against[subject_idx, trial] <- data$player.choice1_against[subj_trial_idx]
            testdataList$choice2with[subject_idx, trial] <- data$player.choice2_with[subj_trial_idx]
            testdataList$choice2against[subject_idx, trial] <- data$player.choice2_against[subj_trial_idx]
        }
    }
}

# Create new list with desired order
testdataList <- testdataList[c(
  "nSubjects",
  "nTrials",
  "choice1",
  "choice2", 
  "chswitch",
  "bet1",
  "bet2",
  "reward",
  "choice1Acc",
  "choice2Acc",
  "winprob",
  "otherChoice1",
  "otherChoice2",
  "otherReward",
  "choice1with",
  "choice1against",
  "choice2with",
  "choice2against",
  "otherChoice1Acc",
  "otherChoice2Acc"
)]

# Save the reordered list
save(testdataList, file = here::here("data", "rdata", "testdata.RData"))

# Load Lei's data for comparison
load(here::here("data", "rdata", "subset_data.RData"))
```







